### 2016-08-08 Writeup/paper.tex
Add basic writeup framework

\documentclass[10pt,twocolumn]{confpaper}

\graphicspath{ {./figures/} }
\newcommand{\system}{{\em NetASM}}

\date{\today}
\title{\ttlfnt{Comparing the performance of websites and their content distribution networks}}
\author{
Jacques Heunis\\
\affaddr{HNSJAC003}
% How do you add multiple authors? >.>
}

\begin{document}

\maketitle

\begin{sloppypar}

\begin{abstract}
\end{abstract}

\section{Introduction}\label{sec:intro}
% http://www-net.cs.umass.edu/kurose/writing/intro-style.html

\section{Related Work}\label{sec:related}
\cite{reich2013modular}

\section{Method}\label{sec:method}

\section{Data?}\label{sec:data} % How is this different from results AND method? >.>

\section{Results}\label{sec:results}

\balance
\section{Future Work}\label{sec:futurework}

\end{sloppypar}

%\vspace{-0.1in}
%\section*{Acknowledgments}
% Comments for people we need to acknowledge in the final version.

\pagebreak

\small
%\setlength{\bibsep}{0pt}
\setlength{\parskip}{-1pt}
\setlength{\itemsep}{-1pt}
% \footnotesize % SPACE
\balance
\bibliographystyle{abbrv}
\bibliography{paper}

\end{document}

### 2016-08-21 findip.py
Write output to csv file for later analysis

@@ -5,6 +5,7 @@ import re
 import requests
 import psutil
 import os
+import csv
 from time import sleep
 
 # Set this to subprocess.DEVNULL for clean output, None for verbose output
@@ -141,21 +142,28 @@ def profileURL(targetURL, localIP, listenDeviceID):
 
     targetIPWhoisDict = whoisIP(targetIP)
     targetIPLocation = (targetIPWhoisDict["region"] + " " + targetIPWhoisDict["country"]).strip()
+    targetIPOwner = targetIPWhoisDict["org"]
     targetIPPing = pingIP(targetIP)
     targetIPRoute = traceRouteToIP(targetIP)
-    print("Target IP ({0} - RTT:{3}ms - {4} hops) location is in {1} and managed by {2}".format(targetIP, targetIPLocation, targetIPWhoisDict["org"], targetIPPing, len(targetIPRoute)))
+    targetData = (targetIP, targetIPLocation, targetIPOwner, targetIPPing, len(targetIPRoute))
+    print("Target IP ({0} - RTT:{3}ms - {4} hops) location is in {1} and managed by {2}".format(targetIP, targetIPLocation, targetIPOwner, targetIPPing, len(targetIPRoute)))
 
     cdnIPWhoisDict = whoisIP(cdnIP)
     cdnIPLocation = (cdnIPWhoisDict["region"] + " " + cdnIPWhoisDict["country"]).strip()
+    cdnIPOwner = cdnIPWhoisDict["org"]
     cdnIPPing = pingIP(cdnIP)
     cdnIPRoute = traceRouteToIP(cdnIP)
-    print("CDN IP ({0} - RTT:{3}ms - {4} hops) location is in {1} and managed by {2}".format(cdnIP, cdnIPLocation, cdnIPWhoisDict["org"], cdnIPPing, len(cdnIPRoute)))
+    cdnData = (cdnIP, cdnIPLocation, cdnIPOwner, cdnIPPing, len(cdnIPRoute))
+    print("CDN IP ({0} - RTT:{3}ms - {4} hops) location is in {1} and managed by {2}".format(cdnIP, cdnIPLocation, cdnIPOwner, cdnIPPing, len(cdnIPRoute)))
 
     contentIPWhoisDict = whoisIP(contentIP)
     contentIPLocation = (contentIPWhoisDict["region"] + " " + contentIPWhoisDict["country"]).strip()
+    contentIPOwner = contentIPWhoisDict["org"]
     contentIPPing = pingIP(contentIP)
[…]

### 2016-08-21 findip.py
Delete existing files instead of continuing the same download
Fixes #2.

@@ -82,6 +82,11 @@ def getIPFromHost(targetHost):
 
 
 def getContentIP(targetURL, localIP, networkDeviceID):
+    downloadFilename = subprocess.check_output(['youtube-dl', '--get-filename', targetURL]).strip().decode()
+    if os.path.isfile(downloadFilename):
+        os.remove(downloadFilename)
+    if os.path.isfile(downloadFilename + ".part"):
+        os.remove(downloadFilename + ".part")
     downloadProcess = subprocess.Popen(['youtube-dl', targetURL], stdout=verboseOutputTarget, stderr=subprocess.STDOUT)
     """
     We're using WinDump, a Windows port of tcpdump (available at https://www.winpcap.org/windump/)

### 2016-08-21 findip.py
Add a ping test to try limit incorrect measurements

@@ -28,9 +28,9 @@ def getPrimaryNetworkDevice():
         packetSniffProcList.append(packetSniffProc)
 
     if sys.platform == 'win32':
-        subprocess.Popen(['ping', '-n', '4', 'www.google.com'], stdout=verboseOutputTarget, stderr=subprocess.STDOUT).wait()
+        subprocess.Popen(['ping', '-n', '4', '8.8.8.8'], stdout=verboseOutputTarget, stderr=subprocess.STDOUT).wait()
     else:
-        subprocess.Popen(['ping', '-c', '4', '-s', '24', 'www.google.com'], stdout=verboseOutputTarget, stderr=subprocess.STDOUT).wait()
+        subprocess.Popen(['ping', '-c', '4', '-s', '24', '8.8.8.8'], stdout=verboseOutputTarget, stderr=subprocess.STDOUT).wait()
     validIDList = []
     for deviceID in range(deviceCount):
         if packetSniffProcList[deviceID].poll() is not None:
@@ -219,6 +219,11 @@ def measureExistingNetworkActivity(sleepTime = 3, thresholdRecvKBs = 100, thresh
     afterRecv = afterIoStat[1]
     if afterRecv - initialRecv > thresholdRecvKBs * 1024 * sleepTime or afterSent - initialSent > thresholdSendKBs * 1024 * sleepTime:
         print("Existing network activity detected, ensure that there is no network activity before executing")
+        sys.exit(1)
+
+    localPing = pingIP("8.8.8.8")
+    if int(localPing) > 150:
+        print("Ping to google DNS is higher than expected, ensure network is stable before executing measurement")
         sys.exit(1)
 
 

### 2016-08-21 findip.py
Support comments and newlines in urls.txt Exit program if network trace is too noisy instead of returning None

@@ -87,6 +87,8 @@ def getContentIP(targetURL, localIP, networkDeviceID):
         os.remove(downloadFilename)
     if os.path.isfile(downloadFilename + ".part"):
         os.remove(downloadFilename + ".part")
+    if os.path.isfile(downloadFilename + ".part-Init"):
+        os.remove(downloadFilename + ".part-Init")
     downloadProcess = subprocess.Popen(['youtube-dl', targetURL], stdout=verboseOutputTarget, stderr=subprocess.STDOUT)
     """
     We're using WinDump, a Windows port of tcpdump (available at https://www.winpcap.org/windump/)
@@ -128,7 +130,8 @@ def getContentIP(targetURL, localIP, networkDeviceID):
             maxIPCount = ipMap[ip]
             maxIP = ip
     if maxIPCount < (len(dumpOutput) - nonMatches) / 2:
-        return None
+        print("The network trace is too noisy in order to determine the content IP")
+        sys.exit(1)
     else:
         return maxIP
 
@@ -240,9 +243,10 @@ def run(inputFilename):
     titleRow += ["contentIP", "contentLoc", "contentOwner", "contentPing", "contentHops"]
     csvWriter.writerow(titleRow)
     for url in inputFile:
-        targetURL = url.strip()
-        urlMetrics = profileURL(targetURL, localIP, listenDeviceID)
-        csvWriter.writerow(urlMetrics[0] + urlMetrics[1] + urlMetrics[2])
+        if url.strip() != '' and not url.startswith('#'):
+            targetURL = url.strip()
+            urlMetrics = profileURL(targetURL, localIP, listenDeviceID)
+            csvWriter.writerow(urlMetrics[0] + urlMetrics[1] + urlMetrics[2])
     inputFile.close()
     outputFile.close()
 

### 2016-08-21 findip.py
Add re-try functionality to getContentIP

@@ -9,7 +9,10 @@ import csv
 from time import sleep
 
 # Set this to subprocess.DEVNULL for clean output, None for verbose output
-verboseOutputTarget = subprocess.DEVNULL
+verboseOutputTarget = None
+
+# Retry attemps
+numberOfRetries = 3
 
 if sys.platform == 'win32':
     dumptool = 'windump'
@@ -83,13 +86,7 @@ def getIPFromHost(targetHost):
 
 def getContentIP(targetURL, localIP, networkDeviceID):
     downloadFilename = subprocess.check_output(['youtube-dl', '--get-filename', targetURL]).strip().decode()
-    if os.path.isfile(downloadFilename):
-        os.remove(downloadFilename)
-    if os.path.isfile(downloadFilename + ".part"):
-        os.remove(downloadFilename + ".part")
-    if os.path.isfile(downloadFilename + ".part-Init"):
-        os.remove(downloadFilename + ".part-Init")
-    downloadProcess = subprocess.Popen(['youtube-dl', targetURL], stdout=verboseOutputTarget, stderr=subprocess.STDOUT)
+
     """
     We're using WinDump, a Windows port of tcpdump (available at https://www.winpcap.org/windump/)
     -n stops it from resolving hostnames (which makes it much faster and we only want IPs anyways)
@@ -101,39 +98,53 @@ def getContentIP(targetURL, localIP, networkDeviceID):
     Specifying tcp just makes it filter out everything that isn't sent via TCP
     """
     dumpArgs = ['-nvS', '-s 128', '-i %d' % networkDeviceID, '-c 3000', 'tcp']
-    dumpProcess = subprocess.Popen([dumptool] + dumpArgs, stdout=subprocess.PIPE, stderr=verboseOutputTarget)
-    dumpOutput = dumpProcess.stdout.readlines()
-    downloadProcess.kill()
 
-    ipMap = {}
-    ipRegex = re.compile(r'((\d+\.){3}\d+)\.\d+ > ((\d+\.){3}\d+)\.\d+')
-    nonMatches = 0
-    for line in dumpOutput:
-        ipMatch = ipRegex.search(str(line))
-        if not ipMatch:
-            nonMatches += 1
-            continue
 
-        sourceIP = ipMatch.group(1)
-        targetIP = ipMatch.group(3)
-        if sourceIP == localIP:
-            continue
-        if sourceIP not in ipMap:
-            ipMap[sourceIP] = 1
-        else:
[…]

### 2016-08-21 findip.py
Reset output to non-verbose

@@ -9,7 +9,7 @@ import csv
 from time import sleep
 
 # Set this to subprocess.DEVNULL for clean output, None for verbose output
-verboseOutputTarget = None
+verboseOutputTarget = subprocess.DEVNULL
 
 # Retry attemps
 numberOfRetries = 3

### 2016-08-21 findip.py
Move retry vebose message

@@ -99,8 +99,11 @@ def getContentIP(targetURL, localIP, networkDeviceID):
     """
     dumpArgs = ['-nvS', '-s 128', '-i %d' % networkDeviceID, '-c 3000', 'tcp']
 
-
     for i in range(numberOfRetries + 1):
+        if i != 0:
+            # Failed to obtain content IP
+            verbosePrint("Re-trying to obtain content IP. Attempt {0} out of {1}.".format(i, numberOfRetries))
+
         if os.path.isfile(downloadFilename):
             os.remove(downloadFilename)
         if os.path.isfile(downloadFilename + ".part"):
@@ -139,9 +142,6 @@ def getContentIP(targetURL, localIP, networkDeviceID):
                 maxIP = ip
         if maxIPCount > (len(dumpOutput) - nonMatches) / 2:
             return maxIP
-
-        # Failed to obtain content IP
-        verbosePrint("Re-trying to obtain content IP. Attempt {0} out of {1}.".format(i + 1, numberOfRetries))
 
     # If we are unable to determine the content IP after the retry attempts, we raise a RunTime exception
     raise RuntimeError("The network trace is too noisy in order to determine the content IP")

### 2016-08-21 findip.py
Remove part files more aggressively

@@ -104,12 +104,8 @@ def getContentIP(targetURL, localIP, networkDeviceID):
             # Failed to obtain content IP
             verbosePrint("Re-trying to obtain content IP. Attempt {0} out of {1}.".format(i, numberOfRetries))
 
-        if os.path.isfile(downloadFilename):
-            os.remove(downloadFilename)
-        if os.path.isfile(downloadFilename + ".part"):
-            os.remove(downloadFilename + ".part")
-        if os.path.isfile(downloadFilename + ".part-Init"):
-            os.remove(downloadFilename + ".part-Init")
+        removePartFiles(downloadFilename)
+
         downloadProcess = subprocess.Popen(['youtube-dl', targetURL], stdout=verboseOutputTarget, stderr=subprocess.STDOUT)
 
         dumpProcess = subprocess.Popen([dumptool] + dumpArgs, stdout=subprocess.PIPE, stderr=verboseOutputTarget)
@@ -141,6 +137,7 @@ def getContentIP(targetURL, localIP, networkDeviceID):
                 maxIPCount = ipMap[ip]
                 maxIP = ip
         if maxIPCount > (len(dumpOutput) - nonMatches) / 2:
+            removePartFiles(downloadFilename)
             return maxIP
 
     # If we are unable to determine the content IP after the retry attempts, we raise a RunTime exception
@@ -263,6 +260,14 @@ def run(inputFilename):
 def verbosePrint(message):
     if verboseOutputTarget is None:
         print(message)
+
+
+def removePartFiles(downloadFilename):
+    currentDir = os.getcwd()
+    files = os.listdir(currentDir)
+    for file in files:
+        if file.endswith(".part") or ".part-" in file or file == downloadFilename:
+            os.remove(os.path.join(currentDir, file))
 
 
 # We can use https://www.reddit.com/r/unknownvideos/ as a source of probably-not-cached videos

### 2016-08-21 Writeup/paper.tex
Make some intial inroads on writeup

@@
-\documentclass[10pt,twocolumn]{confpaper}
+\documentclass{sig-alternate-05-2015}
 
-\graphicspath{ {./figures/} }
-\newcommand{\system}{{\em NetASM}}
+\usepackage{graphicx}
+
+\def\sharedaffiliation{%
+\end{tabular}
+\begin{tabular}{c}}
+
+\begin{document}
+
+	% Copyright
+	\setcopyright{acmcopyright}
+	%\setcopyright{acmlicensed}
+	%\setcopyright{rightsretained}
+	%\setcopyright{usgov}
+	%\setcopyright{usgovmixed}
+	%\setcopyright{cagov}
+	%\setcopyright{cagovmixed}
+
+	% DOI
+	\doi{n/a}
+
+	% ISBN
+	\isbn{n/a}
 
@@
 \author{
-Jacques Heunis\\
-\affaddr{HNSJAC003}
-% How do you add multiple authors? >.>
+	\begin{tabular}{c}
+		% 1st. author
+		Jacques Heunis \\
+		\affaddr{University of Cape Town}\\
+		\email{hnsjac003@myuct.ac.za}
+	\end{tabular}%
+	\begin{tabular}{c}
+		% 2nd. author
+		Brian McGeorge \\
+		\affaddr{University of Cape Town}\\
+		\email{mcgbri004@myuct.ac.za}
+	\end{tabular} 
 }
 
-\begin{document}
-
 \maketitle
-
-\begin{sloppypar}
 
@@
 \section{Introduction}\label{sec:intro}
-% http://www-net.cs.umass.edu/kurose/writing/intro-style.html
+In the modern internet, 65\% of web traffic is handled by just 10 organisations \cite{Gehlen2012}.
+These organisations have to serve tremendous amounts of data to a large user base across the globe.
+Vast Content Delivery Networks (CDN) and data centres are therefore required to serve up all this content.
+Approximately 90\% of Google's traffic and over 50\% of Level3 and Limelight's traffic is from video content alone \cite{Gehlen2012}.
+
+Of the video streaming services on the internet, YouTube is most popular with over a billion users \cite{youtubeStats}.
+Everyday, YouTube generates billions of views with people watching hundreds of million of hours of content \cite{youtubeStats}.
+
+Our aim in this paper is to investigate the performance of the CDN's that serve this content.
+We will examine different streaming services from a variety of South African Internet Service Providers (ISP) to examine how traffic is routed and where it comes from.
+In addition, we will also examine the caching behaviour of YouTube, which has local caches in South Africa.
 
 \section{Related Work}\label{sec:related}
-\cite{reich2013modular}
+% Relevant work that has been done
+Uncovering the Big Players of the Web\\
+Dissecting Video Server Selection Strategies
+in the YouTube CDN\\
+YouTube traffic dynamics and its interplay with a tier-1 ISP: an ISP perspective\\
+When YouTube Does not Work—Analysis of QoE-Relevant Degradation in Google CDN Traffic\\
+Internet Inter-Domain Traffic\\
+YouTube Traffic Characterization: A View From the Edge\\
 
 \section{Method}\label{sec:method}
-
 \section{Data?}\label{sec:data} % How is this different from results AND method? >.>
-
+% Only seems relevent to groups who are using an existing dataset for their work
 \section{Results}\label{sec:results}
-
-\balance
 \section{Future Work}\label{sec:futurework}
-
-\end{sloppypar}
-
-%\vspace{-0.1in}
-%\section*{Acknowledgments}
-% Comments for people we need to acknowledge in the final version.
 
@@
 \small
-%\setlength{\bibsep}{0pt}
-\setlength{\parskip}{-1pt}
-\setlength{\itemsep}{-1pt}
-% \footnotesize % SPACE
-\balance
 \bibliographystyle{abbrv}
-\bibliography{paper}
+\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
 

### 2016-08-21 findip.py
Minor re-ordering in if statement

@@ -266,7 +266,7 @@ def removePartFiles(downloadFilename):
     currentDir = os.getcwd()
     files = os.listdir(currentDir)
     for file in files:
-        if file.endswith(".part") or ".part-" in file or file == downloadFilename:
+        if file.endswith(".part") or file == downloadFilename or ".part-" in file:
             os.remove(os.path.join(currentDir, file))
 
 

### 2016-08-21 findip.py
Change re-try from verbose to regular print instead

@@ -102,7 +102,7 @@ def getContentIP(targetURL, localIP, networkDeviceID):
     for i in range(numberOfRetries + 1):
         if i != 0:
             # Failed to obtain content IP
-            verbosePrint("Re-trying to obtain content IP. Attempt {0} out of {1}.".format(i, numberOfRetries))
+            print("Re-trying to obtain content IP due to noisy trace. Attempt {0} out of {1}.".format(i, numberOfRetries))
 
         removePartFiles(downloadFilename)
 

### 2016-08-22 findip.py
Add tracking of download throughput for the content

@@ -106,11 +106,27 @@ def getContentIP(targetURL, localIP, networkDeviceID):
 
         removePartFiles(downloadFilename)
 
-        downloadProcess = subprocess.Popen(['youtube-dl', targetURL], stdout=verboseOutputTarget, stderr=subprocess.STDOUT)
-
+        downloadProcess = subprocess.Popen(['youtube-dl', targetURL], stdout=subprocess.PIPE, stderr=subprocess.STDOUT)
         dumpProcess = subprocess.Popen([dumptool] + dumpArgs, stdout=subprocess.PIPE, stderr=verboseOutputTarget)
         dumpOutput = dumpProcess.stdout.readlines()
         downloadProcess.kill()
+
+        downloadSpeedOutputLine = downloadProcess.stdout.readlines()[-1].decode()
+        downloadSpeedFinalOutput = downloadSpeedOutputLine[downloadSpeedOutputLine.rfind('\r'):]
+        downloadSpeedUnits = ("B/s", "KiB/s", "MiB/s")
+        downloadKBPerSecond = -1
+        unitFactor = 1.0/1024.0 # NOTE: This is the factor for B/s, and we assume the following units are the next one up each time
+        for units in downloadSpeedUnits:
+            patternString = r"at (\d+\.?\d*)%s ETA" % units
+            downloadSpeedMatch = re.search(patternString, downloadSpeedFinalOutput)
+            if not downloadSpeedMatch:
+                unitFactor *= 1024
+                continue
+            else:
+                downloadKBPerSecond = float(downloadSpeedMatch.group(1)) * unitFactor
+                break
+        if downloadKBPerSecond == -1:
+            print("ERROR: Unable to extract download speed from final output line: %s" % downloadSpeedOutputLine)
 
         ipMap = {}
         ipRegex = re.compile(r'((\d+\.){3}\d+)\.\d+ > ((\d+\.){3}\d+)\.\d+')
@@ -138,7 +154,7 @@ def getContentIP(targetURL, localIP, networkDeviceID):
                 maxIP = ip
         if maxIPCount > (len(dumpOutput) - nonMatches) / 2:
             removePartFiles(downloadFilename)
-            return maxIP
+            return maxIP, downloadKBPerSecond
 
     # If we are unable to determine the content IP after the retry attempts, we raise a RunTime exception
[…]

### 2016-08-22 findip.py
Add retry logic to make code more robust Add timestamp appended to data.csv to prevent overwrite Execute each test case 3 times to improve result accuracy Fix a bug in trace route logic which caused incorrect number of hops

@@ -7,12 +7,16 @@ import psutil
 import os
 import csv
 from time import sleep
+from datetime import datetime
 
 # Set this to subprocess.DEVNULL for clean output, None for verbose output
 verboseOutputTarget = subprocess.DEVNULL
 
 # Retry attemps
 numberOfRetries = 3
+
+# Number of test runs
+numberOfRuns = 3
 
 if sys.platform == 'win32':
     dumptool = 'windump'
@@ -81,7 +85,14 @@ def getHostFromURL(targetURL):
 
 
 def getIPFromHost(targetHost):
-    return socket.gethostbyname(targetHost)
+    for i in range(numberOfRetries + 1):
+        try:
+            return socket.gethostbyname(targetHost.strip())
+        except socket.gaierror:
+            if i < numberOfRetries:
+                continue
+            else:
+                raise
 
 
 def getContentIP(targetURL, localIP, networkDeviceID):
@@ -194,18 +205,18 @@ def profileURL(targetURL, localIP, listenDeviceID):
     contentIPPing = pingIP(contentIP)
     contentIPRoute = traceRouteToIP(contentIP)
     contentData = (contentIP, contentIPLocation, contentIPOwner, contentIPPing, len(contentIPRoute), contentKBPerSecond)
-    print("Content IP ({0} - RTT:{3}ms - {4} hops) location is in {1} and managed by {2}".format(contentIP, contentIPLocation, contentIPOwner, contentIPPing, len(contentIPRoute)))
+    print("Content IP ({0} - RTT:{3}ms - {4} hops) location is in {1} and managed by {2}\n".format(contentIP, contentIPLocation, contentIPOwner, contentIPPing, len(contentIPRoute)))
     return (targetData, cdnData, contentData)
 
 
 def traceRouteToIP(url):
     """Executes a trace route to the argument url or ip.
-    It does not resolve hostnames, is limited to maximum 20 hops
-    and will wait 500 milliseconds before considering a packet dropped."""
+    It does not resolve hostnames, is limited to maximum 30 hops
+    and will wait a maximum of 1500 milliseconds before moving to the next hop."""
     if sys.platform == 'win32':
-        traceOutput = subprocess.check_output([traceTool, "-d", "-h", "20", "-w", "500", url])
+        traceOutput = subprocess.check_output([traceTool, "-d", "-h", "30", "-w", "1500", url])
     else:
[…]

### 2016-08-22 findip.py
Check ping value as float instead of int to support linux ping tool

@@ -270,7 +270,7 @@ def measureExistingNetworkActivity(sleepTime = 3, thresholdRecvKBs = 100, thresh
         raise RuntimeError("Existing network activity detected, ensure that there is no network activity before executing")
 
     localPing = pingIP("8.8.8.8")
-    if int(localPing) > 150:
+    if float(localPing) > 150:
         raise RuntimeError("Ping to google DNS is higher than expected, ensure network is stable before executing measurement")
 
 

### 2016-08-22 Writeup/paper.tex
WIP Report

@@
 Approximately 90\% of Google's traffic and over 50\% of Level3 and Limelight's traffic is from video content alone \cite{Gehlen2012}.
+Labovitz \textit{et al.} \cite{Labovitz:2010:IIT:2043164.1851194} suggests that videos account for $25-40\%$ of all HTTP traffic.
 
@@
 Everyday, YouTube generates billions of views with people watching hundreds of million of hours of content \cite{youtubeStats}.
+With new content constantly getting generated around the world, caching strategies are required so that this content can be served up at a high throughput from as close as possible to the user.
+ISPs play a critical role in this through their peering policies and by providing their own CDNs for various content \cite{Labovitz:2010:IIT:2043164.1851194}.
 
 Our aim in this paper is to investigate the performance of the CDN's that serve this content.
-We will examine different streaming services from a variety of South African Internet Service Providers (ISP) to examine how traffic is routed and where it comes from.
+We will examine different streaming services across a variety of South African Internet Service Providers (ISP) to examine how traffic is routed and where it comes from.
 In addition, we will also examine the caching behaviour of YouTube, which has local caches in South Africa.
+We have developed a tool which automates much of the aforementioned.
+It can take a list of URLs to content at a streaming service and record various performance metrics regarding how the content is delivered to the end-user.
+
+Section \ref{sec:related} will examine related work in measuring the performance of streaming services and studies which investigate the behaviour of CDNs for multimedia streaming services.
+Section \ref{sec:tool} describes the tool that was developed and its features.
+Section \ref{sec:method} describes the steps we followed in capturing our results.
+Section \ref{sec:results} presents the results and infers its meaning.
 
@@
 YouTube traffic dynamics and its interplay with a tier-1 ISP: an ISP perspective\\
-When YouTube Does not Work—Analysis of QoE-Relevant Degradation in Google CDN Traffic\\
+When YouTube Does not Work - Analysis of QoE-Relevant Degradation in Google CDN Traffic\\
 Internet Inter-Domain Traffic\\
@@
 
+% TODOs:
+% 	- add a section on the tool, what it does and how it tries to ensure accuracy and repeatability in our dynamic environment (throughput and ping tests beforehand, repeating each run 3 times, re-try logic to make the code robust etc.
+etc.
+Just sell it!)
+% 	- (Sub?)Section on the data we collect and why this information is useful for our study
 \section{Method}\label{sec:method}
 \section{Data?}\label{sec:data} % How is this different from results AND method? >.>
-% Only seems relevent to groups who are using an existing dataset for their work
 \section{Results}\label{sec:results}

### 2016-08-26 findip.py
Make packet count restriction slightly less strict Reduce the occurace of download speed mismatches

@@ -122,13 +122,15 @@ def getContentIP(targetURL, localIP, networkDeviceID):
         dumpOutput = dumpProcess.stdout.readlines()
         downloadProcess.kill()
 
-        downloadSpeedOutputLine = downloadProcess.stdout.readlines()[-1].decode()
+        downloadLines = downloadProcess.stdout.readlines()
+        downloadSpeedOutputLine = downloadLines[-1].decode()
         downloadSpeedFinalOutput = downloadSpeedOutputLine[downloadSpeedOutputLine.rfind('\r'):]
+
         downloadSpeedUnits = ("B/s", "KiB/s", "MiB/s")
         downloadKBPerSecond = -1
         unitFactor = 1.0/1024.0 # NOTE: This is the factor for B/s, and we assume the following units are the next one up each time
         for units in downloadSpeedUnits:
-            patternString = r"at (\d+\.?\d*)%s ETA" % units
+            patternString = r"(\d+\.?\d*)%s ETA" % units
             downloadSpeedMatch = re.search(patternString, downloadSpeedFinalOutput)
             if not downloadSpeedMatch:
                 unitFactor *= 1024
@@ -136,8 +138,12 @@ def getContentIP(targetURL, localIP, networkDeviceID):
             else:
                 downloadKBPerSecond = float(downloadSpeedMatch.group(1)) * unitFactor
                 break
+
         if downloadKBPerSecond == -1:
-            print("ERROR: Unable to extract download speed from final output line: %s" % downloadSpeedOutputLine)
+            print("{0} - ERROR: Unable to extract download speed from final output line.".format(downloadSpeedOutputLine))
+
+        verbosePrint(downloadSpeedOutputLine)
+        verbosePrint("Download Speed: {0}".format(downloadKBPerSecond))
 
         ipMap = {}
         ipRegex = re.compile(r'((\d+\.){3}\d+)\.\d+ > ((\d+\.){3}\d+)\.\d+')
@@ -163,7 +169,7 @@ def getContentIP(targetURL, localIP, networkDeviceID):
             if ipMap[ip] > maxIPCount:
                 maxIPCount = ipMap[ip]
                 maxIP = ip
-        if maxIPCount > (len(dumpOutput) - nonMatches) / 2:
+        if maxIPCount > (len(dumpOutput) - nonMatches) / 3:
[…]

### 2016-08-26 Writeup/paper.tex
Some minor grammatical updates to the introduction to better fit the structure of the rest of the paper

@@
 In addition, we will also examine the caching behaviour of YouTube, which has local caches in South Africa.
-We have developed a tool which automates much of the aforementioned.
-It can take a list of URLs to content at a streaming service and record various performance metrics regarding how the content is delivered to the end-user.
+We have developed a tool which automates many of the aforementioned measurements.
+It can take a list of URLs to content on a streaming service and record various performance metrics regarding how the content is delivered to the end-user.
 
 Section \ref{sec:related} will examine related work in measuring the performance of streaming services and studies which investigate the behaviour of CDNs for multimedia streaming services.
-Section \ref{sec:tool} describes the tool that was developed and its features.
-Section \ref{sec:method} describes the steps we followed in capturing our results.
-Section \ref{sec:results} presents the results and infers its meaning.
+Section \ref{sec:method} describes the tool that we developed and details the steps we followed in using it to capture our results.
+Section \ref{sec:results} presents the results and a discussion thereof.
 
@@
 \section{Method}\label{sec:method}
+We
+
 \section{Data?}\label{sec:data} % How is this different from results AND method? >.>

### 2016-08-26 Writeup/paper.tex
Fill out the Method section

@@
 \section{Method}\label{sec:method}
-We
+\subsection{Measurement and tools}
+To measure the performance of CDNs, we have created a tool to automatically capture various quantitative and qualitative performance metrics when given a list of URLs to online video or audio content.
+In order to compare the performance of CDNs to that of the websites that present the content, we measure 2 primary quantitative metrics: Ping or Round-trip-time and the number of hops required to reach the server.
+We also measure the throughput to the CDN.
+To gain further insight into the potential causes for variances in performance, we also take note of the location and owner of the web page and CDN IPs.
+
+Our tool is written using Python 3, but makes use of a number of third-party tools and services.
+It makes use of the youtube-dl\footnote{youtube-dl: available at https://rg3.github.io/youtube-dl/} tool to download multimedia content (which is used to measure bandwidth, as detailed below), and uses tcpdump to passively capture network traffic (on Windows we use WinDump which is a Windows port of tcpdump, but for the purposes of this report we will refer to tcpdump).
+The ipinfo.io service\footnote{ipinfo: available at http://ipinfo.io/} is used to gather information about the registered owners of the website and CDN IP addresses.
+
+For each input URL we run youtube-dl and ask that it simply return the URL of the actual content and exit.
+Both URLs are resolved to IP addresses and stored for later measurement.
+We then run tcpdump, specifying that it will terminate after 3000 packets have been received, and then run youtube-dl again.
+This time we let youtube-dl actually download the media file, allowing tcpdump to the required 3000 packets and then terminate.
+At this point we can kill the youtube-dl process and just consider its output.
+First, we look at the last line of output from youtube-dl in order to get the throughput that the content was transmitted at.
+This does mean that we rely on youtube-dl's measurements being accurate, but previous attempts to measure throughput ourselves proved inaccurate as youtube-dl does some work before downloading (for example to get the CDN URL from the webpage).
+
+Next we go through every packet that tcpdump captured and find the IP that sent us the most packets.
+We consider that to be the IP that the content actually came from, as long as more than one third of the captured packets came from that IP.
+Now we have an IP for the website, the CDN, and the actual content, and we run ping and traceroute, as well as querying ipinfo.io for all three of these.
+
+In order to reduce the chance of our results being affected by other applications that might be using the network, we first listen to the existing traffic on the network when the tool first starts up.
+If there is more than 100KB/s of incoming traffic or more than 30KB/s of outgoing traffic, we prompt the user to reduce network traffic and do not proceed with the test.
+This gives our results greater accuracy and repeatability as it prevents us from running the experiment when there is already high-network usage, which would skew the data.
+
+In order to further improve the accuracy of our results, we run each test 3 times for each input URL.
+This prevents a short-running network-intensive process from executing only during one test and leading us to believe that one particular website or piece of content is received significantly more slowly than the others.
+
+\subsection{Sources of multimedia content}
+As mentioned in Section \ref{sec:intro}, Youtube is one of the most popular video streaming services on the internet.
+Since this is not a study of Youtube specifically, we need to gather data on a number of other multimedia streaming services as well.
+We decided to also gather data about the popular music sharing service Soundcloud, as well as the popular live video streaming platform Twitch.tv.
+Note that our analysis is restricted to on-demand multimedia streaming and we do not consider the performance of live streaming services on Youtube or Twitch.tv.
+Note also that we did not include Netflix in our evaluation.
+While Netflix does constitute a large portion of internet video streaming traffic in the US, it is far less popular in South Africa and so its performance is of less importance here.
+
+Of particular interest is the effect of caching on the performance of Youtube videos.
+It is widely known that there are Google caches in South Africa and that local ISPs have their own caches.
+For this reason we specifically included performance evaluations for Youtube videos that are unpopular or have very few views.
+To find such videos, we manually looked through the ``unknownvideos'' section of Reddit\footnote{``/r/unknownvideos - Watch something new'', available at https://www.reddit.com/r/unknownvideos}.
 

### 2016-08-26 Writeup/paper.tex
Add the plain data to the data section

@@
 We consider that to be the IP that the content actually came from, as long as more than one third of the captured packets came from that IP.
+In the event that no single IP was the source of more than one third of the captured packets, we retry up to three times.
+This retry behaviour gives our test greater stability in the face of existing network traffic.
 Now we have an IP for the website, the CDN, and the actual content, and we run ping and traceroute, as well as querying ipinfo.io for all three of these.
@@
 
-\section{Data?}\label{sec:data} % How is this different from results AND method? >.>
+\begin{itemize}
+	\item Different ISPs? \\
+	\item All the same location - CONSISTENCY
+\end{itemize}
+
 \section{Results}\label{sec:results}
+\subsection{Home network}
+We ran our tests on a single home network, gathering measurements for 5 different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) using the same four media URLs\footnote{Unpopular Youtube video: \\ https://www.youtube.com/watch?v=1-xX7hPxMio}\footnote{Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0}\footnote{Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release}\footnote{Twitch.tv video: \\https://www.twitch.tv/dota2ti/v/83400929}.
+Below are the results of each run, averaged across ISPs:
+\vspace{1em} \\
+Ping: \\
+\begin{tabular}{|l|l|c|c|c|} \hline
+Run & Source & Website & CDN & Content \\ \hline
+1 & Unpopular Youtube & 39  & 35  & 56  \\ \hline
+  & Popular Youtube   & 60  & 14  & 14  \\ \hline
+  & Soundcloud        & 161 & 162 & 184 \\ \hline
+  & Twitch.tv         & 198 & 159 & 172 \\ \hline
+2 & Unpopular Youtube & 45  & 14  & 17  \\ \hline
+  & Popular Youtube   & 63  & 14  & 31  \\ \hline
+  & Soundcloud        & 161 & 160 & 165 \\ \hline
+  & Twitch.tv         & 193 & 159 & 181 \\ \hline
+3 & Unpopular Youtube & 31  & 17  & 14  \\ \hline
+  & Popular Youtube   & 31  & 23  & 18  \\ \hline
+  & Soundcloud        & 179 & 171 & 160 \\ \hline
+  & Twitch.tv         & 184 & 159 & 161 \\ \hline
+\end{tabular}
+\vspace{1em} \\
+Number of hops: \\
+\begin{tabular}{|l|l|c|c|c|} \hline
+Run & Source & Website & CDN & Content \\ \hline
+1 & Unpopular Youtube & 10 & 7  & 10 \\ \hline
+  & Popular Youtube   & 10 & 8  & 8  \\ \hline
+  & Soundcloud        & 13 & 18 & 18 \\ \hline
+  & Twitch.tv         & 14 & 14 & 15 \\ \hline
+2 & Unpopular Youtube & 10 & 7  & 7  \\ \hline
+  & Popular Youtube   & 10 & 8  & 8  \\ \hline
+  & Soundcloud        & 13 & 18 & 18 \\ \hline
+  & Twitch.tv         & 13 & 15 & 12 \\ \hline
+3 & Unpopular Youtube & 10 & 7  & 7  \\ \hline
+  & Popular Youtube   & 10 & 8  & 8  \\ \hline
+  & Soundcloud        & 13 & 18 & 18 \\ \hline
+  & Twitch.tv         & 13 & 15 & 13 \\ \hline
+\end{tabular}
+\vspace{1em} \\
+Throughput (KB/s): \\
+\begin{tabular}{|l|l|c|c|c|} \hline
+Run & Source & Content \\ \hline
+1 & Unpopular Youtube & 197.8 \\ \hline
+  & Popular Youtube   & 202.6 \\ \hline
+  & Soundcloud        & 197.9 \\ \hline
+  & Twitch.tv         & 201.2 \\ \hline
+2 & Unpopular Youtube & 201.9 \\ \hline
+  & Popular Youtube   & 197.8 \\ \hline
+  & Soundcloud        & 201.3 \\ \hline
+  & Twitch.tv         & 203.1 \\ \hline
+3 & Unpopular Youtube & 202.8 \\ \hline
+  & Popular Youtube   & 200.4 \\ \hline
+  & Soundcloud        & 203.6 \\ \hline
+  & Twitch.tv         & 204.9 \\ \hline
+\end{tabular}
+
+TODO: Table of "offset from median" of the metrics for each ISP
+
+\subsection{UCT Network}
+For a comparison, we also ran two tests on the UCT network. The test was run from a laptop connected to the UCT network via Ethernet.
+
+Note that some of the throughput data points are missing, this is because we measure throughput as youtube-dl downloads and in those cases the download finished before we could get a good measure.
+\subsubsection{Test case 1}
+The first test case used the following media URLs:
+\begin{itemize}
+	\item Unpopular Youtube video: \\ https://www.youtube.com/watch?v=nKETYT-2NY8
+	\item Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0
+	\item Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release
+	\item Twitch.tv video: \\ https://www.twitch.tv/dota2ti/v/83400929
+\end{itemize}
+The results are tabulated below:
+\vspace{1em} \\
+Ping: \\
+\begin{tabular}{|l|l|c|c|c|} \hline
+Run & Source & Website & CDN & Content \\ \hline
+1 & Unpopular Youtube & 18  & 49  & 44  \\ \hline
+  & Popular Youtube   & 45  & 19  & 18  \\ \hline
+  & Soundcloud        & 179 & 148 & 154 \\ \hline
+  & Twitch.tv         & 148 & 155 & 148 \\ \hline
+2 & Unpopular Youtube & 21  & 19  & 19  \\ \hline
+  & Popular Youtube   & 19  & 26  & 19  \\ \hline
+  & Soundcloud        & 148 & 149 & 148 \\ \hline
+  & Twitch.tv         & 148 & 148 & 148 \\ \hline
+3 & Unpopular Youtube & 3   & 19  & 19  \\ \hline
+  & Popular Youtube   & 2   & 45  & 68  \\ \hline
+  & Soundcloud        & 148 & 148 & 148 \\ \hline
+  & Twitch.tv         & 151 & 154 & 148 \\ \hline
+\end{tabular}
+\vspace{1em} \\
+Number of hops: \\
+\begin{tabular}{|l|l|c|c|c|} \hline
+Run & Source & Website & CDN & Content \\ \hline
+1 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
+  & Popular Youtube   & 9 & 9 & 9 \\ \hline
+  & Soundcloud        & 9 & 9 & 9 \\ \hline
+  & Twitch.tv         & 9 & 9 & 9 \\ \hline
+2 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
+  & Popular Youtube   & 9 & 9 & 9 \\ \hline
+  & Soundcloud        & 9 & 9 & 9 \\ \hline
+  & Twitch.tv         & 9 & 9 & 9 \\ \hline
+3 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
+  & Popular Youtube   & 9 & 9 & 9 \\ \hline
+  & Soundcloud        & 9 & 9 & 9 \\ \hline
+  & Twitch.tv         & 9 & 9 & 9 \\ \hline
+\end{tabular}
+\vspace{1em} \\
+Throughput: \\
+\begin{tabular}{|l|l|c|c|c|} \hline
+Run & Source & Content \\ \hline
+1 & Unpopular Youtube & 1484.8  \\ \hline
+  & Popular Youtube   & 8560.6  \\ \hline
+  & Soundcloud        & 1351.7  \\ \hline
+  & Twitch.tv         & 11284.5 \\ \hline
+2 & Unpopular Youtube & 7690.2  \\ \hline
+  & Popular Youtube   & 8161.3  \\ \hline
+  & Soundcloud        & -       \\ \hline
+  & Twitch.tv         & 11264.0 \\ \hline
+3 & Unpopular Youtube & 7598.1  \\ \hline
+  & Popular Youtube   & 9543.7  \\ \hline
+  & Soundcloud        & -       \\ \hline  
+  & Twitch.tv         & 11233.3 \\ \hline
+\end{tabular}
+
+\subsubsection{Test case 2}
+The second test case used the following media URLs:
+\begin{itemize}
+	\item Unpopular Youtube video: \\ https://www.youtube.com/watch?v=nKETYT-2NY8
+	\item Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0
+	\item Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release
+	\item Twitch.tv video: \\ https://www.twitch.tv/dota2ti/v/83400929
+\end{itemize}
+The results are tabulated below:
+\vspace{1em} \\
+Ping: \\
+\begin{tabular}{|l|l|c|c|c|} \hline
+Run & Source & Website & CDN & Content \\ \hline
+1 & Unpopular Youtube & 4   & 19  & 188 \\ \hline
+  & Popular Youtube   & 4   & 19  & 21  \\ \hline
+  & Twitch.tv         & 148 & 154 & 148 \\ \hline
+  & Soundcloud        & 148 & 148 & 0   \\ \hline
+2 & Unpopular Youtube & 3   & 47  & 19  \\ \hline
+  & Popular Youtube   & 4   & 20  & 19  \\ \hline
+  & Twitch.tv         & 172 & 154 & 0   \\ \hline
+  & Soundcloud        & 148 & 149 & 149 \\ \hline
+3 & Unpopular Youtube & 4   & 33  & 19  \\ \hline
+  & Popular Youtube   & 3   & 20  & 18  \\ \hline
+  & Twitch.tv         & 149 & 148 & 0   \\ \hline
+  & Soundcloud        & 148 & 148 & 148 \\ \hline
+\end{tabular}
+\vspace{1em} \\
+Number of hops: \\
+\begin{tabular}{|l|l|c|c|c|} \hline
+Run & Source & Website & CDN & Content \\ \hline
+1 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
+  & Popular Youtube   & 9 & 9 & 9 \\ \hline
+  & Twitch.tv         & 9 & 9 & 9 \\ \hline
+  & Soundcloud        & 9 & 9 & 1 \\ \hline
+2 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
+  & Popular Youtube   & 9 & 9 & 9 \\ \hline
+  & Twitch.tv         & 9 & 9 & 9 \\ \hline
+  & Soundcloud        & 9 & 9 & 1 \\ \hline
+3 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
+  & Popular Youtube   & 9 & 9 & 9 \\ \hline
+  & Twitch.tv         & 9 & 9 & 9 \\ \hline
+  & Soundcloud        & 9 & 9 & 1 \\ \hline
+\end{tabular}
+\vspace{1em} \\
+Throughput: \\
+\begin{tabular}{|l|l|c|c|c|} \hline
+Run & Source & Content \\ \hline
+1 & Unpopular Youtube & 190.9   \\ \hline
+  & Popular Youtube   & 8048.6  \\ \hline
+  & Twitch.tv         & 10526.7 \\ \hline
+  & Soundcloud        & 1341.4  \\ \hline
+2 & Unpopular Youtube & 9513.0  \\ \hline
+  & Popular Youtube   & 8335.4  \\ \hline
+  & Twitch.tv         & 11397.1 \\ \hline
+  & Soundcloud        & -       \\ \hline
+3 & Unpopular Youtube & 9840.6  \\ \hline
+  & Popular Youtube   & 7260.2  \\ \hline
+  & Twitch.tv         & 11274.2 \\ \hline  
+  & Soundcloud        & -       \\ \hline
+\end{tabular}
+
 \section{Future Work}\label{sec:futurework}
+\begin{itemize}
+	\item Streaming (e.g incorporate youtube life or twitch non-vods)
+	\item Video content vs video adverts
+	\item Test from multiple locations
+\end{itemize}
 

### 2016-08-26 Writeup/paper.tex
Add a 'Measurement Location' subsection to Method

@@
 
-\begin{itemize}
-	\item Different ISPs? \\
-	\item All the same location - CONSISTENCY
-\end{itemize}
+\subsection{Measurement Location}
+We measure two different scenarios: Home networks and Institutional networks.
+In the case of home networks, all our measurements were done from the same location (in order to ensure consistency in our results).
+Home network measurements were taken while connected to five different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) for comparison.
+
+In the case of institutional networks, all our measurements were done while connected to the UCT network.
+This test was added in order to compare the results from a home network to what one might get on a network with significantly higher bandwidth.
 

### 2016-08-26 findip.py
Fix issues with linux traceroute

@@ -224,9 +224,9 @@ def traceRouteToIP(url):
     if sys.platform == 'win32':
         traceOutput = subprocess.check_output([traceTool, "-d", "-h", "30", "-w", "1500", url])
     else:
-        traceOutput = subprocess.check_output([traceTool, "-n", "-m", "30", "-w", "1.5", url, "32"])
+        traceOutput = subprocess.check_output([traceTool,"--icmp" , "-n", "-m", "30", "-w", "1.5", url, "32"])
     traceStr = traceOutput.decode()
-    hopExpr = re.compile(r'^\s+\d+')
+    hopExpr = re.compile(r'^\s*\d+')
     traceLines = [l for l in traceStr.split(os.linesep) if hopExpr.match(l) is not None]
     return traceLines
 

### 2016-08-26 Writeup/paper.tex
Added some comments

@@
 \subsection{Measurement and tools}
+% Possible improvements / modifications:
+% "owner of the web page" -> organisation hosting the webpage?
+% Why 3000 packets?
+% We also do a ping test at the start to ensure that latency is in a reasonable range (< 150 ms)
+%
+%
+
 To measure the performance of CDNs, we have created a tool to automatically capture various quantitative and qualitative performance metrics when given a list of URLs to online video or audio content.
@@
 We then run tcpdump, specifying that it will terminate after 3000 packets have been received, and then run youtube-dl again.
-This time we let youtube-dl actually download the media file, allowing tcpdump to the required 3000 packets and then terminate.
+This time we let youtube-dl actually download the media file, allowing tcpdump to capture the required 3000 packets and then terminate.
 At this point we can kill the youtube-dl process and just consider its output.
@@
 \subsection{Home network}
+% We are missing the caching train in this section wrt unpopular video (since the same video is used)
+% Telkom is first -> EU -> Telkom -> Telkom
+% Then ISP 2 is second -> Google Cache -> ISP 2 -> ISP 2
+% Then ISP 3 is third -> Google Cache -> ISP 3 -> ISP 3
+% Then ISP 4 is fourth but uses same backbone as ISP 3 so -> ISP 3 -> ISP 3 -> ISP 3 etc.
+
 We ran our tests on a single home network, gathering measurements for 5 different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) using the same four media URLs\footnote{Unpopular Youtube video: \\ https://www.youtube.com/watch?v=1-xX7hPxMio}\footnote{Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0}\footnote{Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release}\footnote{Twitch.tv video: \\https://www.twitch.tv/dota2ti/v/83400929}.

### 2016-08-27 Writeup/paper.tex
Make comment more clear
Additional comment
Add some missing points to the measurement method

@@
 
-% TODOs:
-% 	- add a section on the tool, what it does and how it tries to ensure accuracy and repeatability in our dynamic environment (throughput and ping tests beforehand, repeating each run 3 times, re-try logic to make the code robust etc.
-etc.
-Just sell it!)
-% 	- (Sub?)Section on the data we collect and why this information is useful for our study
 \section{Method}\label{sec:method}
 \subsection{Measurement and tools}
-% Possible improvements / modifications:
-% "owner of the web page" -> organisation hosting the webpage?
-% Why 3000 packets?
-% We also do a ping test at the start to ensure that latency is in a reasonable range (< 150 ms)
-%
+% We should mention that on testing YouTube dl performed the same as streaming through browser.
 %
@@
 We also measure the throughput to the CDN.
-To gain further insight into the potential causes for variances in performance, we also take note of the location and owner of the web page and CDN IPs.
+To gain further insight into the potential causes for variances in performance, we also take note of the location and hosting organisation of the web page and CDN IPs.
+The source code for our tool is publicly available on GitHub\footnote{CDNPerf -  https://github.com/jacquesh/cdnperf}.
 
@@
 It makes use of the youtube-dl\footnote{youtube-dl: available at https://rg3.github.io/youtube-dl/} tool to download multimedia content (which is used to measure bandwidth, as detailed below), and uses tcpdump to passively capture network traffic (on Windows we use WinDump which is a Windows port of tcpdump, but for the purposes of this report we will refer to tcpdump).
-The ipinfo.io service\footnote{ipinfo: available at http://ipinfo.io/} is used to gather information about the registered owners of the website and CDN IP addresses.
+The ipinfo.io service\footnote{ipinfo: available at http://ipinfo.io/} is used to gather information about the organisation that is hosting the website and CDN IP addresses.
 
@@
 Both URLs are resolved to IP addresses and stored for later measurement.
-We then run tcpdump, specifying that it will terminate after 3000 packets have been received, and then run youtube-dl again.
-This time we let youtube-dl actually download the media file, allowing tcpdump to capture the required 3000 packets and then terminate.
+We then run tcpdump, specifying that it will terminate after 3000 packets have been received.
+This is just to gather enough packets that we can be fairly sure that our results are not contaminated by another process using the network at an unfortunate time.
+We then run youtube-dl again, but this time we let it actually download the media file, allowing tcpdump to capture the required 3000 packets and then terminate.
 At this point we can kill the youtube-dl process and just consider its output.
@@
 
-In order to reduce the chance of our results being affected by other applications that might be using the network, we first listen to the existing traffic on the network when the tool first starts up.
-If there is more than 100KB/s of incoming traffic or more than 30KB/s of outgoing traffic, we prompt the user to reduce network traffic and do not proceed with the test.
+In order to reduce the chance of our results being affected by other applications that might be using the network, we first ping Google's 8.8.8.8 DNS server and listen to the existing traffic on the network when the tool first starts up.
+If we get a round-trip time of over 150ms or there is more than 100KB/s of incoming traffic or more than 30KB/s of outgoing traffic, we prompt the user to reduce network traffic and do not proceed with the test.
 This gives our results greater accuracy and repeatability as it prevents us from running the experiment when there is already high-network usage, which would skew the data.
@@
 % We are missing the caching train in this section wrt unpopular video (since the same video is used)
-% Telkom is first -> EU -> Telkom -> Telkom
-% Then ISP 2 is second -> Google Cache -> ISP 2 -> ISP 2
-% Then ISP 3 is third -> Google Cache -> ISP 3 -> ISP 3
+% This is another reason why 3 tests are run, it makes this caching behaviour clear
+% Telkom is first -> EU Google Cache -> Telkom -> Telkom
+% Then ISP 2 is second -> SA Google Cache -> ISP 2 -> ISP 2
+% Then ISP 3 is third -> SA Google Cache -> ISP 3 -> ISP 3
 % Then ISP 4 is fourth but uses same backbone as ISP 3 so -> ISP 3 -> ISP 3 -> ISP 3 etc.

### 2016-08-27 Writeup/paper.tex
Add explanation of higher ping on run 1

@@
 \subsection{Home network}
+% Maybe run a speed test so we can quote the results and give perspective for our result numbers?
+
 % We are missing the caching train in this section wrt unpopular video (since the same video is used)
@@
 
+\vspace{1em}
 TODO: Table of "offset from median" of the metrics for each ISP
+\vspace{1em}
+
+It is immediately clear that the throughput does not differ much across websites or runs, although this is not unexpected given the relatively low bandwidth of the home connection.
+Another trend which is immediately clear is the significant difference between ping and number of hops to Youtube and Soundcloud/Twitch.tv.
+This is simply because Youtube content is cached within South Africa while Twitch.tv and Soundcloud do not, most likely because they are not large enough to be able to afford setting up expensive caches all over the world.
+
+One thing that is less obvious is the difference of the first run to the other two for the unpopular Youtube video.
+In runs 2 and 3 the actual content came from an IP with approximately the same ping and hops as the CDN, but in run 1 it both are significantly higher.
+The cause of this is clear if we look at the ping to the content IP for only that URL across ISPs:
+\vspace{1em} \\
+\begin{tabular}{|l|c|c|c|c|c|} \hline
+Run & Afrihost & Axxess & Cybersmart & Telkom & WebAfrica \\ \hline
+1 & 11 & 11  & 34  & 197 & 27 \\ \hline
+2 & 11 & 11  & 12  & 9   & 42 \\ \hline
+3 & 11 & 11  & 12  & 9   & 26 \\ \hline
+\end{tabular}
+These results are expected if we consider that the tests were done by doing 3 runs on Telkom first, followed by WebAfrica, Cybersmart, Axxess and finally Afrihost.
+On the first run (which just happens to be via Telkom) the video is not cached, so we get it from a server that is outside South Africa.
+This causes it to get cached however, causing the following runs to serve the content from a server that is much closer to the user.
+
+One more thing to notice is that in most cases, the ping to the website is higher than to the CDN or the content.
+This is a useful result as it indicates that content delivery networks are providing an optimized means of delivering high-bandwidth content to users.
 

### 2016-08-27 Writeup/paper.tex
Add ISP-specific data and some discussion

@@
 We ran our tests on a single home network, gathering measurements for 5 different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) using the same four media URLs\footnote{Unpopular Youtube video: \\ https://www.youtube.com/watch?v=1-xX7hPxMio}\footnote{Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0}\footnote{Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release}\footnote{Twitch.tv video: \\https://www.twitch.tv/dota2ti/v/83400929}.
+
+\subsubsection{Results across ISPs}
 Below are the results of each run, averaged across ISPs:
@@
 This is a useful result as it indicates that content delivery networks are providing an optimized means of delivering high-bandwidth content to users.
+
+\subsubsection{Results across runs}
+To investigate the differences between ISPs, we present below the offset from the median ping and throughput averaged across the 3 runs:
+\vspace{1em} \\
+Offset from median ping to website (ms, lower is better): \\
+\begin{tabular}{|l|c|c|c|c|c|} \hline
+ & \small{Afrihost} & \small{Axxess} & \small{Cybersmart} & \small{Telkom} & \small{WebAfrica} \\ \hline
+\small{Unpopular YT} & 9  & 23  & 2  & -1  & -3 \\ \hline
+Popular YT           & 11 & 88  & 1  & -1  & -6 \\ \hline
+Soundcloud           & 10 & 0   & -5 & -3  & 53 \\ \hline
+Twitch.tv            & 26 & 6   & 14 & -9  & 41 \\ \hline
+Total                & 56 & 117 & 12 & -14 & 85 \\ \hline
+\end{tabular}
+\vspace{1em} \\
+Offset from median ping to CDN (ms, lower is better): \\
+\begin{tabular}{|l|c|c|c|c|c|} \hline
+ & \small{Afrihost} & \small{Axxess} & \small{Cybersmart} & \small{Telkom} & \small{WebAfrica} \\ \hline
+\small{Unpopular YT} & 35 & -1 & 0  & -2 & 21 \\ \hline
+Popular YT           & 0  & 0  & 0  & -2 & 28 \\ \hline
+Soundcloud           & 14 & 2  & -6 & -1 & 25 \\ \hline
+Twitch.tv            & -5 & -4 & 1  & 1  & 12 \\ \hline
+Total                & 44 & -4 & -4 & -3 & 86 \\ \hline
+\end{tabular}
+\vspace{1em} \\
+Offset from median ping to content (ms, lower is better): \\
+\begin{tabular}{|l|c|c|c|c|c|} \hline
+ & \small{Afrihost} & \small{Axxess} & \small{Cybersmart} & \small{Telkom} & \small{WebAfrica} \\ \hline
+\small{Unpopular YT} & -5  & -5 & 3  & 56 & 15 \\ \hline
+Popular YT           & 0   & 7  & 0  & -2 & 45 \\ \hline
+Soundcloud           & -8  & -1 & 2  & -1 & 52 \\ \hline
+Twitch.tv            & 0   & 29 & -3 & 15 & 16 \\ \hline
+Total                & -14 & 29 & 2  & 68 & 129 \\ \hline
+\end{tabular}
+\vspace{1em} \\
+Offset from median throughput (KB/s, higher is better): \\
+\begin{tabular}{|l|c|c|c|c|c|} \hline
+ & \small{Afrihost} & \small{Axxess} & \small{Cybersmart} & \small{Telkom} & \small{WebAfrica} \\ \hline
+\small{Unpopular YT} & 1.5  & -0.5  & 2.1   & -3.9 & -2.9 \\ \hline
+Popular YT           & -0.8 & -8.5  & -3.1  & 0.4  & -1.2 \\ \hline
+Soundcloud           & 0.1  & -5.1  & -1.3  & 2.5  & -5.4 \\ \hline
+Twitch.tv            & -0.4 & 0.3   & -6.8  & 0.7  & -0.6 \\ \hline
+Total                & 0.4  & -13.8 & -9.2  & -0.3 & -10.2\\ \hline
+\end{tabular}
+\vspace{1em} \\
+While the different ISPs clearly perform differently, the only significant trend is that WebAfrica consistently gave a higher ping, although still less than 100ms, suggesting that the caches for WebAfrica are still within South Africa but not in Cape Town (for example, they could be in Johannesburg).
+The differences in throughput are not significant and while there are some significant differences in latency, they are not consistent and so are likely due to external factors on the network.
 
@@
 \vspace{1em} \\
-Number of hops: \\
+Number of hops: \\ % TODO: Update these with correct values
 \begin{tabular}{|l|l|c|c|c|} \hline
@@
 
+\subsubsection{Discussions}
+Being a significantly higher-bandwidth connection than what is available to a home user, this test over UCT's network makes the effects of caching and performance of CDNs more pronounced.
+The Youtube web page  gets served at a much lower ping than the actual content, suggesting that the web page is being cached within UCT's network.
+Also note the difference in throughput for the unpopular Youtube video on the first run to the other runs.
+On run 1 the video is not cached (as is evident by the higher ping) and is delivered at a far lower throughput than on subsequent or than the popular Youtube video.
+
+Another point of particular interest is the very low ping and hop counts that appear in test case 2.
+The results show the test machine's IP as the IP that the content was being retrieved from.
+This is most likely a bug in our tool's parsing of tcpdump's output.
+
 \section{Future Work}\label{sec:futurework}

### 2016-08-27 Writeup/paper.tex
Fill out the Future work section

@@
 \section{Future Work}\label{sec:futurework}
-\begin{itemize}
-	\item Streaming (e.g incorporate youtube life or twitch non-vods)
-	\item Video content vs video adverts
-	\item Test from multiple locations
-\end{itemize}
+Our experiments have focussed on streaming of internet video and audio on-demand, from websites including Youtube, Twitch.tv and Soundcloud.
+In future work we would like to extend this to streaming of live video and audio content such as from Youtube Live or Twitch.tv's live streams.
+Another extension would be to consider the differences in performance of streamed video content to video adverts, which are prevalent both on Youtube and Twitch.tv.
 
-\pagebreak
+Another direction that would be useful in future work is to run a more distributed version of our experiments which include running the test from various locations around the world.
+This would give a better understanding of how our results generalize to the internet as a whole, rather than just the connectivity in South Africa.
 

### 2016-08-27 Writeup/paper.tex
Add first draft of related work

@@
 % Relevant work that has been done
-Uncovering the Big Players of the Web\\
-Dissecting Video Server Selection Strategies
-in the YouTube CDN\\
-YouTube traffic dynamics and its interplay with a tier-1 ISP: an ISP perspective\\
-When YouTube Does not Work - Analysis of QoE-Relevant Degradation in Google CDN Traffic\\
-Internet Inter-Domain Traffic\\
-YouTube Traffic Characterization: A View From the Edge\\
+There have been a number of studies on how the performance of video streaming affects the quality of experience (QoE) for the user.
+Casas \textit{et al.} \cite{6975242} took an ISP traffic view by analysing 1 months worth of YouTube packet flows from a large European ISP.
+The study challenges Google's Video Quality Report \footnote{http://www.google.com/get/videoqualityreport/} as it only considers ISP and access link bottlenecks as the root cause of bad user experience \cite{6975242}.
+Casas \textit{et al.} \cite{6975242} presents how poor content server selection by Google resulted in a large scale reduction for in QoE for many YouTube users.
+Fiadino \textit{et al.} \cite{6932930} developed an tool for ISP's to detect unexpected cache-selection events and changes in the traffic delivered by CDNs.
+As such, anomalous CDN behaviour can have a large impact for ISP's carrying the traffic and end-users \cite{6932930, Plissonneau:2012:LVH:2155555.2155588}.
+Zhu \textit{et al.} \cite{6233056} developed LatLong, a tool for CDN's to diagnose large latency increases on the network through passive measurement of traffic and routing.
+Results from analysing a one month's data from Google's CDN show that more than 40\% of latency increases coincide with interdomain routing changes and more than one-third involve a shift in traffic to different servers.
+Juluri \textit{et al.} \cite{6038496} developed a tool to measure playback quality on an end-host.
+The tool captures various metrics such as delay towards the server, download
+rates, and buffering duration \cite{6038496}. These can then be used to measure Quality of Experience.
+
+In 2007 Gill \textit{et al.} \cite{Gill:2007:YTC:1298306.1298310} studied the usage patterns, file properties, popularity and transfer behaviour of YouTube.
+Its findings found that caching could be used effectively to scale Web 2.0 applications such as YouTube \cite{Gill:2007:YTC:1298306.1298310}.In 2011, Torres \textit{et al.} \cite{5961681} analysed a week-long dataset collected from the edge of five networks.
+The study determined the location of YouTube servers and revealed that round trip time (RTT) is not the only factor determining video server selection \cite{5961681}.
+Other factors that were found to affect server selection were load-balancing, the DNS server used and popularity of the accessed video \cite{5961681}.
+
+Labovitz \textit{et al.} \cite{Labovitz:2010:IIT:2043164.1851194} analysed 2 years worth of internet traffic through 110 different cable operators, international transit backbones, regional networks and content providers.
+The study found that there was a significant rise in video traffic and that the majority of inter-domain traffic flows directly between large content providers, CDNs and consumer networks.
 

### 2016-08-27 Writeup/paper.tex
Make tables smaller font

@@
 Ping: \\
+{\small
 \begin{tabular}{|l|l|c|c|c|} \hline
@@
   & Twitch.tv         & 184 & 159 & 161 \\ \hline
-\end{tabular}
+\end{tabular}}
 \vspace{1em} \\
 Number of hops: \\
+{\small
 \begin{tabular}{|l|l|c|c|c|} \hline
@@
   & Twitch.tv         & 13 & 15 & 13 \\ \hline
-\end{tabular}
+\end{tabular}}
 \vspace{1em} \\
 Throughput (KB/s): \\
+{\small
 \begin{tabular}{|l|l|c|c|c|} \hline
@@
   & Twitch.tv         & 204.9 \\ \hline
-\end{tabular}
+\end{tabular}}
 
@@
 \vspace{1em} \\
+{\small
 \begin{tabular}{|l|c|c|c|c|c|} \hline
@@
 3 & 11 & 11  & 12  & 9   & 26 \\ \hline
-\end{tabular}
+\end{tabular}}
 These results are expected if we consider that the tests were done by doing 3 runs on Telkom first, followed by WebAfrica, Cybersmart, Axxess and finally Afrihost.
@@
 Offset from median ping to website (ms, lower is better): \\
+{\small
 \begin{tabular}{|l|c|c|c|c|c|} \hline
@@
 Total                & 56 & 117 & 12 & -14 & 85 \\ \hline
-\end{tabular}
+\end{tabular}}
 \vspace{1em} \\
 Offset from median ping to CDN (ms, lower is better): \\
+{\small
 \begin{tabular}{|l|c|c|c|c|c|} \hline
@@
 Total                & 44 & -4 & -4 & -3 & 86 \\ \hline
-\end{tabular}
+\end{tabular}}
 \vspace{1em} \\
 Offset from median ping to content (ms, lower is better): \\
+{\small
 \begin{tabular}{|l|c|c|c|c|c|} \hline
@@
 Total                & -14 & 29 & 2  & 68 & 129 \\ \hline
-\end{tabular}
+\end{tabular}}
 \vspace{1em} \\
 Offset from median throughput (KB/s, higher is better): \\
+{\small
 \begin{tabular}{|l|c|c|c|c|c|} \hline
@@
 Total                & 0.4  & -13.8 & -9.2  & -0.3 & -10.2\\ \hline
-\end{tabular}
+\end{tabular}}
 \vspace{1em} \\
@@
   & Twitch.tv         & 151 & 154 & 148 \\ \hline
-\end{tabular}
+\end{tabular}}
 \vspace{1em} \\
 Number of hops: \\
+{\small
 \begin{tabular}{|l|l|c|c|c|} \hline
@@
   & Twitch.tv         & 9 & 9 & 9 \\ \hline
-\end{tabular}
+\end{tabular}}
 \vspace{1em} \\
 Throughput: \\
+{\small
 \begin{tabular}{|l|l|c|c|c|} \hline
@@
   & Twitch.tv         & 11233.3 \\ \hline
-\end{tabular}
+\end{tabular}}
 
@@
   & Soundcloud        & 148 & 148 & 148 \\ \hline
-\end{tabular}
+\end{tabular}}
 \vspace{1em} \\
 Number of hops: \\ % TODO: Update these with correct values
+{\small
 \begin{tabular}{|l|l|c|c|c|} \hline
@@
   & Soundcloud        & 9 & 9 & 1 \\ \hline
-\end{tabular}
+\end{tabular}}
 \vspace{1em} \\
 Throughput: \\
+{\small
 \begin{tabular}{|l|l|c|c|c|} \hline
@@
   & Soundcloud        & -       \\ \hline
-\end{tabular}
+\end{tabular}}
 

### 2016-08-28 Writeup/paper.tex
Clean up tables to be slightly less messy

--- 2016-08-27 Writeup/paper.tex
@@
 \subsubsection{Results across ISPs}
-Below are the results of each run, averaged across ISPs:
-\vspace{1em} \\
-Ping: \\
+Table \ref{table:avgPingAcrossISP}, \ref{table:avgHopsAcrossISP} and \ref{avgThroughputAcrossISP} show the ping, number of hops and throughput averaged across ISPs.
+\begin{table}
+	\centering
+	\caption{Averaged ping across ISPs}
+	\label{table:avgPingAcrossISP}
+	\makebox[\linewidth]{
+	\small
 	\begin{tabular}{|l|l|c|c|c|} \hline
@@
 	  & Twitch.tv         & 184 & 159 & 161 \\ \hline
-\end{tabular}
-\vspace{1em} \\
-Number of hops: \\
+	\end{tabular}}
+\end{table}
+
+\begin{table}
+	\centering
+	\caption{Averaged number of hops across ISPs}
+	\label{table:avgHopsAcrossISP}
+	\makebox[\linewidth]{
+	\small
 	\begin{tabular}{|l|l|c|c|c|} \hline
@@
 	  & Twitch.tv         & 13 & 15 & 13 \\ \hline
-\end{tabular}
-\vspace{1em} \\
-Throughput (KB/s): \\
+	\end{tabular}}
+\end{table}
+
+\begin{table}
+	\centering
+	\caption{Averaged throughput (KB/s) across ISPs}
+	\label{avgThroughputAcrossISP}
+	\makebox[\linewidth]{
+	\small
 	\begin{tabular}{|l|l|c|c|c|} \hline
@@
 	  & Twitch.tv         & 204.9 \\ \hline
-\end{tabular}
-
-\vspace{1em}
-TODO: Table of "offset from median" of the metrics for each ISP
-\vspace{1em}
-
+	\end{tabular}}
+\end{table}
+% TODO: Table of "offset from median" of the metrics for each ISP
 It is immediately clear that the throughput does not differ much across websites or runs, although this is not unexpected given the relatively low bandwidth of the home connection.
@@
 In runs 2 and 3 the actual content came from an IP with approximately the same ping and hops as the CDN, but in run 1 it both are significantly higher.
-The cause of this is clear if we look at the ping to the content IP for only that URL across ISPs:
-\vspace{1em} \\
+The cause of this is clear if we look at Table \ref{table:LatencyToUnpopularYouTubeVideo} which shows the ping to the content IP for only that URL across ISPs.
+
+\begin{table}
+	\centering
+	\caption{Latency to unpopular YouTube video}
+	\label{table:LatencyToUnpopularYouTubeVideo}
+	\makebox[\linewidth]{
+	\small
 	\begin{tabular}{|l|c|c|c|c|c|} \hline
@@
 	3 & 11 & 11  & 12  & 9   & 26 \\ \hline
-\end{tabular}
+	\end{tabular}}
+\end{table}
 These results are expected if we consider that the tests were done by doing 3 runs on Telkom first, followed by WebAfrica, Cybersmart, Axxess and finally Afrihost.
@@
 \subsubsection{Results across runs}
-To investigate the differences between ISPs, we present below the offset from the median ping and throughput averaged across the 3 runs:
-\vspace{1em} \\
-Offset from median ping to website (ms, lower is better): \\
+To investigate the differences between ISPs, we present below the offset from the median ping and throughput averaged across the 3 runs.
+Table \ref{table:OffsetFromMedianPingToWebsite}, \ref{table:OffsetFromMedianPingToCDN} and \ref{table:OffsetFromMedianPingToContent} contain the offset from median ping to website, CDN and content IP from each ISP respectively.
+Table \ref{table:OffsetFromMedianThroughput} contains the offset median throughput for each ISP.
+
+\begin{table}
+	\centering
+	\caption{Offset from median ping to website (ms, lower is better)}
+	\label{table:OffsetFromMedianPingToWebsite}
+	\makebox[\linewidth]{
+	\small
 	\begin{tabular}{|l|c|c|c|c|c|} \hline
@@
 	Total                & 56 & 117 & 12 & -14 & 85 \\ \hline
-\end{tabular}
-\vspace{1em} \\
-Offset from median ping to CDN (ms, lower is better): \\
+	\end{tabular}}
+\end{table}
+
+\begin{table}
+	\centering
+	\caption{Offset from median ping to CDN (ms, lower is better)}
+	\label{table:OffsetFromMedianPingToCDN}
+	\makebox[\linewidth]{
+	\small
 	\begin{tabular}{|l|c|c|c|c|c|} \hline
@@
 	Total                & 44 & -4 & -4 & -3 & 86 \\ \hline
-\end{tabular}
-\vspace{1em} \\
-Offset from median ping to content (ms, lower is better): \\
+	\end{tabular}}
+\end{table}
+
+\begin{table}
+	\centering
+	\caption{Offset from median ping to content (ms, lower is better)}
+	\label{table:OffsetFromMedianPingToContent}
+	\makebox[\linewidth]{
+	\small
 	\begin{tabular}{|l|c|c|c|c|c|} \hline
@@
 	Total                & -14 & 29 & 2  & 68 & 129 \\ \hline
-\end{tabular}
-\vspace{1em} \\
-Offset from median throughput (KB/s, higher is better): \\
+	\end{tabular}}
+\end{table}
+
+\begin{table}
+	\centering
+	\caption{Offset from median throughput (KB/s, higher is better)}
+	\label{table:OffsetFromMedianThroughput}
+	\makebox[\linewidth]{
+	\small
 	\begin{tabular}{|l|c|c|c|c|c|} \hline
@@
 	Total                & 0.4  & -13.8 & -9.2  & -0.3 & -10.2\\ \hline
-\end{tabular}
-\vspace{1em} \\
+	\end{tabular}}
+\end{table}
 While the different ISPs clearly perform differently, the only significant trend is that WebAfrica consistently gave a higher ping, although still less than 100ms, suggesting that the caches for WebAfrica are still within South Africa but not in Cape Town (for example, they could be in Johannesburg).
+% Can you expand the above statement. What is less than 100ms? Because twitch and soundcloud is always in EU > 100ms.
 The differences in throughput are not significant and while there are some significant differences in latency, they are not consistent and so are likely due to external factors on the network.
@@
 \end{itemize}
-The results are tabulated below:
-\vspace{1em} \\
-Ping: \\
+Table \ref{table:UCTPingTests-TestCase1}, \ref{table:UCTHopCount-TestCase1} and \ref{table:UCTThroughput-TestCase1} contain the ping, number of hops and throughput for each run of test case 1.
+
+\begin{table}
+	\centering
+	\caption{Ping using UCT network}
+	\label{table:UCTPingTests-TestCase1}
+	\makebox[\linewidth]{
+	\small
 	\begin{tabular}{|l|l|c|c|c|} \hline
@@
 	  & Twitch.tv         & 151 & 154 & 148 \\ \hline
-\end{tabular}
-\vspace{1em} \\
-Number of hops: \\
+	\end{tabular}}
+\end{table}
+
+\begin{table}
+	\centering
+	\caption{Hop count using UCT network}
+	\label{table:UCTHopCount-TestCase1}
+	\makebox[\linewidth]{
+	\small
 	\begin{tabular}{|l|l|c|c|c|} \hline
@@
 	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
-\end{tabular}
-\vspace{1em} \\
-Throughput: \\
+	\end{tabular}}
+\end{table}
+
+\begin{table}
+	\centering
+	\caption{Throughput using UCT network}
+	\label{table:UCTThroughput-TestCase1}
+	\makebox[\linewidth]{
+	\small
 	\begin{tabular}{|l|l|c|c|c|} \hline
@@
 	  & Twitch.tv         & 11233.3 \\ \hline
-\end{tabular}
+	\end{tabular}}
+\end{table}
 
@@
 \end{itemize}
-The results are tabulated below:
-\vspace{1em} \\
-Ping: \\
+Table \ref{table:UCTPing-TestCase2}, \ref{table:UCTHopCount-TestCase2} and \ref{table:UCTThroughput-TestCase2} contain the ping, number of hops and throughput for run of test case 2.
+
+\begin{table}
+	\centering
+	\caption{Ping using UCT network}
+	\label{table:UCTPing-TestCase2}
+	\makebox[\linewidth]{
+	\small
 	\begin{tabular}{|l|l|c|c|c|} \hline
@@
 	  & Soundcloud        & 148 & 148 & 148 \\ \hline
-\end{tabular}
-\vspace{1em} \\
-Number of hops: \\ % TODO: Update these with correct values
+	\end{tabular}}
+\end{table}
+
+\begin{table}
+	\centering
+	\caption{Hop count using UCT network}
+	\label{table:UCTHopCount-TestCase2}
+	\makebox[\linewidth]{
+	\small
+	% TODO: Update these with correct values
 	\begin{tabular}{|l|l|c|c|c|} \hline
@@
 	  & Soundcloud        & 9 & 9 & 1 \\ \hline
-\end{tabular}
-\vspace{1em} \\
-Throughput: \\
+	\end{tabular}}
+\end{table}
+
+\begin{table}
+	\centering
+	\caption{Throughput using UCT network}
+	\label{table:UCTThroughput-TestCase2}
+	\makebox[\linewidth]{
+	\small
 	\begin{tabular}{|l|l|c|c|c|} \hline
@@
 	  & Soundcloud        & -       \\ \hline
-\end{tabular}
+	\end{tabular}}
+\end{table}
 

### 2016-08-28 Writeup/paper.tex
Add baseline ISP speed test results

@@
 \subsection{Home network}
-% Maybe run a speed test so we can quote the results and give perspective for our result numbers?
+%TODO (Jacques) I think it might be good to analyse the WHOIS organisation for Twitch and Soundcloud.
+Is the same organisation serving up the content for each ISP?
+Who is serving up the content for these two services?
 
-% We are missing the caching train in this section wrt unpopular video (since the same video is used)
-% This is another reason why 3 tests are run, it makes this caching behaviour clear
-% Telkom is first -> EU Google Cache -> Telkom -> Telkom
-% Then ISP 2 is second -> SA Google Cache -> ISP 2 -> ISP 2
-% Then ISP 3 is third -> SA Google Cache -> ISP 3 -> ISP 3
-% Then ISP 4 is fourth but uses same backbone as ISP 3 so -> ISP 3 -> ISP 3 -> ISP 3 etc.
+% TODO (Brian) Maybe run a speed test so we can quote the results and give perspective for our result numbers?
 
@@
 
+The Telkom account is a 2 Mbit uncapped account, the rest are 1 GB capped accounts.
+
 \subsubsection{Results across ISPs}
 Table \ref{table:avgPingAcrossISP}, \ref{table:avgHopsAcrossISP} and \ref{avgThroughputAcrossISP} show the ping, number of hops and throughput averaged across ISPs.
+
 \begin{table}
-	\centering
 	\caption{Averaged ping across ISPs}
@@
 \begin{table}
-	\centering
 	\caption{Averaged number of hops across ISPs}
@@
 \begin{table}
-	\centering
 	\caption{Averaged throughput (KB/s) across ISPs}
@@
 One thing that is less obvious is the difference of the first run to the other two for the unpopular Youtube video.
-In runs 2 and 3 the actual content came from an IP with approximately the same ping and hops as the CDN, but in run 1 it both are significantly higher.
-The cause of this is clear if we look at Table \ref{table:LatencyToUnpopularYouTubeVideo} which shows the ping to the content IP for only that URL across ISPs.
+In runs 2 and 3 the actual content came from the same organisation that hosts the CDN, but in run 1 we see significant increase in latency and note that the content comes from a different organisation.
+The cause of this is clear if we look at Table \ref{table:LatencyToUnpopularYouTubeVideo} and \ref{table:OrgHostingUnpopularYouTubeVideo} which shows the ping to the content IP and the organisation that manages it.
 
 \begin{table}
-	\centering
 	\caption{Latency to unpopular YouTube video}
@@
 \end{table}
-These results are expected if we consider that the tests were done by doing 3 runs on Telkom first, followed by WebAfrica, Cybersmart, Axxess and finally Afrihost.
-On the first run (which just happens to be via Telkom) the video is not cached, so we get it from a server that is outside South Africa.
-This causes it to get cached however, causing the following runs to serve the content from a server that is much closer to the user.
+
+\begin{table*}
+	\centering
+	\caption{Organisation managing IP to unpopular YouTube video}
+	\label{table:OrgHostingUnpopularYouTubeVideo}
+	\makebox[\linewidth]{
+		\small
+		\begin{tabular}{|l|c|c|c|c|c|} \hline
+			Run & Afrihost & Axxess & Cybersmart & Telkom & WebAfrica \\ \hline
+			1 & Dimension Data - Optinet & Dimension Data - Optinet & Google Inc. & Google Inc. & Google Inc. \\ \hline
+			2 & Dimension Data - Optinet & Dimension Data - Optinet & Dimension Data - Optinet & Telkom SA Ltd. & Internet Solutions \\ \hline
+			3 & Dimension Data - Optinet & Dimension Data - Optinet & Dimension Data - Optinet & Telkom SA Ltd. & Internet Solutions \\ \hline
+		\end{tabular}}
+	\end{table*}
+
+The tests were done by doing 3 runs on Telkom first, followed by WebAfrica, Cybersmart, Axxess and finally Afrihost to the same unpopular video.
+On the first run (which just happens to be via Telkom) the video is not cached anywhere in South Africa, as a result it has to come from a Google cache in Europe.
+However, this causes it to get cached so the following runs get served from Telkom's own cache.
+What we see from WebAfrica in the subsequent run is that the video does not come from Europe or Telkom's cache.
+It instead comes from a Google cache in South Africa.
+This means that when we first retrieved the video, it was cached not only to Telkom's servers, but also to Google's South African servers.
+Both WebAfrica and Cybersmart first serve the video up using Google's South African cache then serve it up using their respective ISP cache.
+Since Afrihost and Axxess use the same ISP cache as Cybersmart, they are served up directly with the ISP cache in their subsequent runs.
+
+A follow-up test was done to check if Telkom also saw this behaviour that they will fetch a video from Google's South African cache if a user from another South African ISP has watched that video but a Telkom user has not.
+This was found to be the case
 
@@
 To investigate the differences between ISPs, we present below the offset from the median ping and throughput averaged across the 3 runs.
+Table \ref{table:baselineSpeedTests} contains the results from executing a speed test\footnote{Executed at: http://www.speedtest.net} for each ISP.
+This provides some baseline results for each ISP.
 Table \ref{table:OffsetFromMedianPingToWebsite}, \ref{table:OffsetFromMedianPingToCDN} and \ref{table:OffsetFromMedianPingToContent} contain the offset from median ping to website, CDN and content IP from each ISP respectively.
@@
 \begin{table}
-	\centering
+	\caption{Baseline speed test for each ISP}
+	\label{table:baselineSpeedTests}
+	\makebox[75mm]{
+	\small
+	\begin{tabular}{|l|c|c|c|} \hline
+		ISP & \small{Ping (ms)} & \small{Downstream (KB/s)} & \small{UpStream (KB/s)} \\ \hline
+		Afrihost   & 9   & 220    & 51.25 \\ \hline
+		Axxess     & 10  & 221.25 & 55 \\ \hline
+		Cybersmart & 10  & 218.75 & 53.75 \\ \hline
+		Telkom     & 12  & 215    & 43.75 \\ \hline
+		WebAfrica  & 10  & 221.25 & 56.25 \\ \hline
+		\textbf{\textit{Average}}  & \textbf{\textit{10.2}}  & \textbf{\textit{219.25}} & \textbf{\textit{52}} \\ \hline
+	\end{tabular}}
+\end{table}
+
+\begin{table}
 	\caption{Offset from median ping to website (ms, lower is better)}
 	\label{table:OffsetFromMedianPingToWebsite}
-	\makebox[\linewidth]{
+	\makebox[75mm]{
 	\small
@@
 \begin{table}
-	\centering
 	\caption{Offset from median ping to CDN (ms, lower is better)}
 	\label{table:OffsetFromMedianPingToCDN}
-	\makebox[\linewidth]{
+	\makebox[75mm]{
 	\small
@@
 \begin{table}
-	\centering
 	\caption{Offset from median ping to content (ms, lower is better)}
 	\label{table:OffsetFromMedianPingToContent}
-	\makebox[\linewidth]{
+	\makebox[75mm]{
 	\small
@@
 \begin{table}
-	\centering
 	\caption{Offset from median throughput (KB/s, higher is better)}
 	\label{table:OffsetFromMedianThroughput}
-	\makebox[\linewidth]{
+	\makebox[75mm]{
 	\small
@@
 \bibliographystyle{abbrv}
-\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
+\bibliography{paper}
 

### 2016-08-28 findip.py
Fix multiple issues which result in inaccurate results on Linux

@@ -10,7 +10,7 @@ from time import sleep
 from datetime import datetime
 
 # Set this to subprocess.DEVNULL for clean output, None for verbose output
-verboseOutputTarget = subprocess.DEVNULL
+verboseOutputTarget = None
 
 # Retry attemps
 numberOfRetries = 3
@@ -67,7 +67,7 @@ def getLocalIP():
         return localIP
     else:
         ipRoute = subprocess.Popen(["ip", "route", "get", "8.8.8.8"], stdout=subprocess.PIPE)
-        return subprocess.check_output(["awk", "{print $NF; exit}"], stdin=ipRoute.stdout).strip()
+        return subprocess.check_output(["awk", "{print $NF; exit}"], stdin=ipRoute.stdout).strip().decode()
 
 
 def getContentURL(targetURL):
@@ -157,6 +157,7 @@ def getContentIP(targetURL, localIP, networkDeviceID):
             sourceIP = ipMatch.group(1)
             targetIP = ipMatch.group(3)
             if sourceIP == localIP:
+                nonMatches += 1
                 continue
             if sourceIP not in ipMap:
                 ipMap[sourceIP] = 1
@@ -169,7 +170,21 @@ def getContentIP(targetURL, localIP, networkDeviceID):
             if ipMap[ip] > maxIPCount:
                 maxIPCount = ipMap[ip]
                 maxIP = ip
-        if maxIPCount > (len(dumpOutput) - nonMatches) / 2:
+
+        secondIP = ''
+        secondIPCount = 0
+        for ip in ipMap:
+            if ip != maxIP and ipMap[ip] > secondIPCount:
+                secondIPCount = ipMap[ip]
+                secondIP = ip
+
+        totalIPsConsidered = len(dumpOutput) - nonMatches
+        verbosePrint("Local IP - {0}".format(localIP))
+        verbosePrint("Total IPs considered - {0}".format(totalIPsConsidered))
+        verbosePrint("Max IP and count: {0} - {1}".format(maxIP, maxIPCount))
+        verbosePrint("Second IP and count: {0} - {1}".format(secondIP, secondIPCount))
+
+        if maxIPCount > totalIPsConsidered / 2:
             removePartFiles(downloadFilename)
             return maxIP, downloadKBPerSecond
 
@@ -278,6 +293,7 @@ def measureExistingNetworkActivity(sleepTime = 3, thresholdRecvKBs = 100, thresh
[…]

### 2016-08-28 findip.py
Set output to DEVNULL again

@@ -10,7 +10,7 @@ from time import sleep
 from datetime import datetime
 
 # Set this to subprocess.DEVNULL for clean output, None for verbose output
-verboseOutputTarget = None
+verboseOutputTarget = subprocess.DEVNULL
 
 # Retry attemps
 numberOfRetries = 3

### 2016-08-28 findip.py
Remove debug print statement

@@ -293,7 +293,6 @@ def measureExistingNetworkActivity(sleepTime = 3, thresholdRecvKBs = 100, thresh
         raise RuntimeError("Existing network activity detected, ensure that there is no network activity before executing")
 
     localPing = pingIP("8.8.8.8")
-    print(localPing)
     if float(localPing) > 150:
         raise RuntimeError("Ping to google DNS is higher than expected, ensure network is stable before executing measurement")
 

### 2016-08-28 Writeup/paper.tex
Minor sentence improvement
Improve sentence structure Add UCT ethernet speed

@@
 
-We ran our tests on a single home network, gathering measurements for 5 different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) using the same four media URLs\footnote{Unpopular Youtube video: \\ https://www.youtube.com/watch?v=1-xX7hPxMio}\footnote{Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0}\footnote{Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release}\footnote{Twitch.tv video: \\https://www.twitch.tv/dota2ti/v/83400929}.
-
-The Telkom account is a 2 Mbit uncapped account, the rest are 1 GB capped accounts.
+We ran our tests on a single home network, gathering measurements for 5 different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) using the same four media URLs\footnote{Unpopular Youtube video: \\ https://www.youtube.com/watch?v=1-xX7hPxMio}\footnote{Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0}\footnote{Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release}\footnote{Twitch.tv video: \\https://www.twitch.tv/dota2ti/v/83400929} on a 2 megabits per second (Mbps) ADSL line from Telkom.
+The Telkom account is uncapped while the rest of the accounts are capped at 1 gigabyte.
 
@@
 
-The tests were done by doing 3 runs on Telkom first, followed by WebAfrica, Cybersmart, Axxess and finally Afrihost to the same unpopular video.
+The tests did 3 runs on Telkom first, followed by WebAfrica, Cybersmart, Axxess and finally Afrihost to the same unpopular video.
 On the first run (which just happens to be via Telkom) the video is not cached anywhere in South Africa, as a result it has to come from a Google cache in Europe.
@@
 \subsection{UCT Network}
-For a comparison, we also ran two tests on the UCT network. The test was run from a laptop connected to the UCT network via Ethernet.
+For a comparison, we also ran two tests on the UCT network. The test was run from a laptop connected to the UCT network via Ethernet running at 100 Mbps.
 

### 2016-08-28 findip.py
Fix an issue with detection of localIP in Windows

@@ -10,7 +10,7 @@ from time import sleep
 from datetime import datetime
 
 # Set this to subprocess.DEVNULL for clean output, None for verbose output
-verboseOutputTarget = subprocess.DEVNULL
+verboseOutputTarget = None
 
 # Retry attemps
 numberOfRetries = 3
@@ -60,11 +60,12 @@ def getLocalIP():
         ipconfigLines = subprocess.Popen(['ipconfig'], stdout=subprocess.PIPE, stderr=verboseOutputTarget).stdout.readlines()
         localIP = '(Unknown)'
         for line in ipconfigLines:
-            lineStr = str(line.strip())
-            if not lineStr.startswith('IPv4 Address'):
+            lineStr = str(line.decode().strip())
+            index = lineStr.find('IPv4 Address')
+            if index == -1:
                 continue
             localIP = lineStr[lineStr.find(':') + 2:]
-        return localIP
+        return localIP.strip()
     else:
         ipRoute = subprocess.Popen(["ip", "route", "get", "8.8.8.8"], stdout=subprocess.PIPE)
         return subprocess.check_output(["awk", "{print $NF; exit}"], stdin=ipRoute.stdout).strip().decode()

### 2016-08-28 cdn_perf.py
Rename findip.py to cdn_perf.py

@@ -340,6 +340,6 @@ def removePartFiles(downloadFilename):
 # We can use https://www.reddit.com/r/unknownvideos/ as a source of probably-not-cached videos
 if __name__ == '__main__':
     if len(sys.argv) < 2:
-        print('No argument given, expected "findip.py <contentUrl>"')
+        print('No argument given, expected "cdn_perf.py <contentUrl>"')
     else:
         run(sys.argv[1])

### 2016-08-28 cdn_perf.py
Fix spelling error in cdn_perf.py

@@ -12,7 +12,7 @@ from datetime import datetime
 # Set this to subprocess.DEVNULL for clean output, None for verbose output
 verboseOutputTarget = subprocess.DEVNULL
 
-# Retry attemps
+# Retry attempts
 numberOfRetries = 3
 
 # Number of test runs

### 2016-08-28 cdn_perf.py
Minor refactor to getLocalIP()

@@ -56,19 +56,21 @@ def getPrimaryNetworkDevice():
 
 
 def getLocalIP():
+    localIP = '(Unknown)'
     if sys.platform == 'win32':
         ipconfigLines = subprocess.Popen(['ipconfig'], stdout=subprocess.PIPE, stderr=verboseOutputTarget).stdout.readlines()
-        localIP = '(Unknown)'
         for line in ipconfigLines:
             lineStr = str(line.decode().strip())
             index = lineStr.find('IPv4 Address')
             if index == -1:
                 continue
             localIP = lineStr[lineStr.find(':') + 2:]
-        return localIP.strip()
     else:
         ipRoute = subprocess.Popen(["ip", "route", "get", "8.8.8.8"], stdout=subprocess.PIPE)
-        return subprocess.check_output(["awk", "{print $NF; exit}"], stdin=ipRoute.stdout).strip().decode()
+        localIP = subprocess.check_output(["awk", "{print $NF; exit}"], stdin=ipRoute.stdout).strip().decode()
+
+    verbosePrint("Local IP - {0}".format(localIP))
+    return localIP.strip()
 
 
 def getContentURL(targetURL):
@@ -180,7 +182,6 @@ def getContentIP(targetURL, localIP, networkDeviceID):
                 secondIP = ip
 
         totalIPsConsidered = len(dumpOutput) - nonMatches
-        verbosePrint("Local IP - {0}".format(localIP))
         verbosePrint("Total IPs considered - {0}".format(totalIPsConsidered))
         verbosePrint("Max IP and count: {0} - {1}".format(maxIP, maxIPCount))
         verbosePrint("Second IP and count: {0} - {1}".format(secondIP, secondIPCount))

### 2016-08-28 Writeup/paper.tex
Add a subsection on the different servers that ISPs get their Twitch content from

--- 2016-08-28 Writeup/paper.tex
@@
 The differences in throughput are not significant and while there are some significant differences in latency, they are not consistent and so are likely due to external factors on the network.
+
+\subsubsection{Content server owners}
+Although not shown in the tables, it is worth noting the results of the WHOIS lookup for the IPs that served the content.
+In the case of Youtube, which server provides the content depends on which networks make use of which local caches as well as whether or not the requested content is available in the cache.
+This is expected as Youtube is a very popular source of content and ISPs setup complex caching systems to reduce bandwidth.
+For Soundcloud and Twitch.tv however, this is not the case.
+All Soundcloud content gets delivered from a IP address that is registered to Amazon, suggesting that Soundcloud uses Amazon Web Services for all of its content storage and distribution.
+The content servers for Twitch.tv are not as consistent.
+While Afrihost, Telkom and WebAfrica all receive Twitch content from an IP registered to ``MCI Communications Services'' (the same company that is the registered owner of the CDN that hosts the content), Axxess and Cybersmart do not.
+Axxess routes to a CDN owned by MCI, but the actual content comes from a server owned by ``Akamai International''.
+Cybersmart does not even receive Twitch content from the same server each time, content arrives from serves that are owned by a variety of other companies.
 

### 2016-08-28 Writeup/paper.tex
Update the UCT test data tables

@@
 \begin{itemize}
-	\item Unpopular Youtube video: \\ https://www.youtube.com/watch?v=nKETYT-2NY8
-	\item Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0
+	\item Unpopular Youtube video: \\ 
+	https://www.youtube.com/watch?v=yRfwRsJrMzI
+	\item Popular Youtube video: \\
+	https://www.youtube.com/watch?v=9bZkp7q19f0
 	\item Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release
@@
     \centering
-	\caption{Ping using UCT network}
+    \caption{Ping using UCT network - Test 1}
     \label{table:UCTPingTests-TestCase1}
@@
     Run & Source & Website & CDN & Content \\ \hline
-	1 & Unpopular Youtube & 18  & 49  & 44  \\ \hline
-	  & Popular Youtube   & 45  & 19  & 18  \\ \hline
-	  & Soundcloud        & 179 & 148 & 154 \\ \hline
-	  & Twitch.tv         & 148 & 155 & 148 \\ \hline
-	2 & Unpopular Youtube & 21  & 19  & 19  \\ \hline
-	  & Popular Youtube   & 19  & 26  & 19  \\ \hline
-	  & Soundcloud        & 148 & 149 & 148 \\ \hline
+    1 & Unpopular Youtube & 19  & 18  & 184 \\ \hline
+      & Popular Youtube   & 18  & 18  & 18  \\ \hline
       & Twitch.tv         & 148 & 148 & 148 \\ \hline
-	3 & Unpopular Youtube & 3   & 19  & 19  \\ \hline
-	  & Popular Youtube   & 2   & 45  & 68  \\ \hline
-	  & Soundcloud        & 148 & 148 & 148 \\ \hline
-	  & Twitch.tv         & 151 & 154 & 148 \\ \hline
+      & Soundcloud        & 148 & 149 & 149 \\ \hline
+    2 & Unpopular Youtube & 19  & 18  & 18  \\ \hline
+      & Popular Youtube   & 19  & 18  & 19  \\ \hline
+      & Twitch.tv         & 148 & 150 & 153 \\ \hline
+      & Soundcloud        & 148 & 148 & 192 \\ \hline
+    3 & Unpopular Youtube & 19  & 19  & 18  \\ \hline
+      & Popular Youtube   & 19  & 18  & 18  \\ \hline
+      & Twitch.tv         & 148 & 152 & 148 \\ \hline
+      & Soundcloud        & 148 & 149 & 150 \\ \hline
     \end{tabular}}
@@
 	\centering
-	\caption{Hop count using UCT network}
+	\caption{Hop count using UCT network - Test 1}
 	\label{table:UCTHopCount-TestCase1}
@@
     Run & Source & Website & CDN & Content \\ \hline
-	1 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
+    1 & Unpopular Youtube & 9 & 9 & 16 \\ \hline
       & Popular Youtube   & 9 & 9 & 9 \\ \hline
-	  & Soundcloud        & 9 & 9 & 9 \\ \hline
-	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
-	2 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
+      & Twitch.tv         & 13 & 11 & 11 \\ \hline
+      & Soundcloud        & 11 & 18 & 18 \\ \hline
+    2 & Unpopular Youtube & 10 & 9 & 9 \\ \hline
+      & Popular Youtube   & 10 & 9 & 9 \\ \hline
+      & Twitch.tv         & 12 & 13 & 13 \\ \hline
+      & Soundcloud        & 11 & 17 & 17 \\ \hline
+    3 & Unpopular Youtube & 10 & 9 & 9 \\ \hline
       & Popular Youtube   & 9 & 9 & 9 \\ \hline
-	  & Soundcloud        & 9 & 9 & 9 \\ \hline
-	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
-	3 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
-	  & Popular Youtube   & 9 & 9 & 9 \\ \hline
-	  & Soundcloud        & 9 & 9 & 9 \\ \hline
-	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
+      & Twitch.tv         & 13 & 13 & 13 \\ \hline
+      & Soundcloud        & 11 & 18 & 18 \\ \hline
     \end{tabular}}
@@
 	\centering
-	\caption{Throughput using UCT network}
+	\caption{Throughput using UCT network - Test 1}
 	\label{table:UCTThroughput-TestCase1}
@@
     Run & Source & Content    \\ \hline
-	1 & Unpopular Youtube & 1484.8  \\ \hline
-	  & Popular Youtube   & 8560.6  \\ \hline
-	  & Soundcloud        & 1351.7  \\ \hline
-	  & Twitch.tv         & 11284.5 \\ \hline
-	2 & Unpopular Youtube & 7690.2  \\ \hline
-	  & Popular Youtube   & 8161.3  \\ \hline
+    1 & Unpopular Youtube & 521.5  \\ \hline
+      & Popular Youtube   & 9809.9 \\ \hline
+      & Twitch.tv         & 11366.4    \\ \hline
       & Soundcloud        & -    \\ \hline
-	  & Twitch.tv         & 11264.0 \\ \hline
-	3 & Unpopular Youtube & 7598.1  \\ \hline
-	  & Popular Youtube   & 9543.7  \\ \hline
+    2 & Unpopular Youtube & 6481.9  \\ \hline
+      & Popular Youtube   & 9840.6  \\ \hline
+      & Twitch.tv         & 3440.6    \\ \hline
       & Soundcloud        & -    \\ \hline
-	  & Twitch.tv         & 11233.3 \\ \hline
+    3 & Unpopular Youtube & 8069.1  \\ \hline
+      & Popular Youtube   & 9881.6 \\ \hline
+      & Twitch.tv         & 11335.7    \\ \hline
+      & Soundcloud        & -    \\ \hline
     \end{tabular}}
@@
 \begin{itemize}
-	\item Unpopular Youtube video: \\ https://www.youtube.com/watch?v=nKETYT-2NY8
-	\item Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0
+	\item Unpopular Youtube video: \\ 
+	https://www.youtube.com/watch?v=tSzaFuCxjs0
+	\item Popular Youtube video: \\
+	https://www.youtube.com/watch?v=9bZkp7q19f0
 	\item Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release
@@
 	\centering
-	\caption{Ping using UCT network}
+	\caption{Ping using UCT network - Test 2}
 	\label{table:UCTPing-TestCase2}
@@
     Run & Source & Website & CDN & Content \\ \hline
-	1 & Unpopular Youtube & 4   & 19  & 188 \\ \hline
-	  & Popular Youtube   & 4   & 19  & 21  \\ \hline
-	  & Twitch.tv         & 148 & 154 & 148 \\ \hline
-	  & Soundcloud        & 148 & 148 & 0   \\ \hline
-	2 & Unpopular Youtube & 3   & 47  & 19  \\ \hline
-	  & Popular Youtube   & 4   & 20  & 19  \\ \hline
-	  & Twitch.tv         & 172 & 154 & 0   \\ \hline
-	  & Soundcloud        & 148 & 149 & 149 \\ \hline
-	3 & Unpopular Youtube & 4   & 33  & 19  \\ \hline
-	  & Popular Youtube   & 3   & 20  & 18  \\ \hline
-	  & Twitch.tv         & 149 & 148 & 0   \\ \hline
+    1 & Unpopular Youtube & 19 & 3 & 182  \\ \hline
+      & Popular Youtube   & 19 & 18 & 18  \\ \hline
+      & Twitch.tv         & 148 & 150 & 148  \\ \hline
       & Soundcloud        & 148 & 148 & 148  \\ \hline
+    2 & Unpopular Youtube & 19 & 3 & 3  \\ \hline
+      & Popular Youtube   & 19 & 18 & 18  \\ \hline
+      & Twitch.tv         & 148 & 150 & 150  \\ \hline
+      & Soundcloud        & 148 & 148 & 148  \\ \hline
+    3 & Unpopular Youtube & 19 & 3 & 3  \\ \hline
+      & Popular Youtube   & 20 & 18 & 18 \\ \hline
+      & Twitch.tv         & 148 & 148 & 148  \\ \hline
+      & Soundcloud        & 148 & 149 & 148  \\ \hline
     \end{tabular}}	
@@
 	\centering
-	\caption{Hop count using UCT network}
+	\caption{Hop count using UCT network - Test 2}
 	\label{table:UCTHopCount-TestCase2}
@@
 	\small
-	% TODO: Update these with correct values
     \begin{tabular}{|l|l|c|c|c|} \hline
     Run & Source & Website & CDN & Content \\ \hline
-	1 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
+    1 & Unpopular Youtube & 9 & 7 & 16  \\ \hline
+      & Popular Youtube   & 10 & 9 & 9  \\ \hline
+      & Twitch.tv         & 12 & 13 & 13  \\ \hline
+      & Soundcloud        & 11 & 17 & 17  \\ \hline
+    2 & Unpopular Youtube & 10 & 7 & 7  \\ \hline
       & Popular Youtube   & 9 & 9 & 9  \\ \hline
-	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
-	  & Soundcloud        & 9 & 9 & 1 \\ \hline
-	2 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
+      & Twitch.tv         & 13 & 13 & 13  \\ \hline
+      & Soundcloud        & 11 & 16 & 16  \\ \hline
+    3 & Unpopular Youtube & 10 & 7 & 7  \\ \hline
       & Popular Youtube   & 9 & 9 & 9  \\ \hline
-	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
-	  & Soundcloud        & 9 & 9 & 1 \\ \hline
-	3 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
-	  & Popular Youtube   & 9 & 9 & 9 \\ \hline
-	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
-	  & Soundcloud        & 9 & 9 & 1 \\ \hline
+      & Twitch.tv         & 12 & 12 & 12  \\ \hline
+      & Soundcloud        & 11 & 18 & 18  \\ \hline
     \end{tabular}}
@@
 	\centering
-	\caption{Throughput using UCT network}
+	\caption{Throughput using UCT network - Test 2}
 	\label{table:UCTThroughput-TestCase2}
@@
     Run & Source & Content    \\ \hline
-	1 & Unpopular Youtube & 190.9   \\ \hline
-	  & Popular Youtube   & 8048.6  \\ \hline
-	  & Twitch.tv         & 10526.7 \\ \hline
-	  & Soundcloud        & 1341.4  \\ \hline
-	2 & Unpopular Youtube & 9513.0  \\ \hline
-	  & Popular Youtube   & 8335.4  \\ \hline
+    1 & Unpopular Youtube & 1525.8 \\ \hline
+      & Popular Youtube   & 9799.7 \\ \hline
+      & Twitch.tv         & 11427.8 \\ \hline
+      & Soundcloud        & - \\ \hline
+    2 & Unpopular Youtube & 4331.5 \\ \hline
+      & Popular Youtube   & 9820.2 \\ \hline
       & Twitch.tv         & 11397.1 \\ \hline
       & Soundcloud        & - \\ \hline
-	3 & Unpopular Youtube & 9840.6  \\ \hline
-	  & Popular Youtube   & 7260.2  \\ \hline
-	  & Twitch.tv         & 11274.2 \\ \hline  
-	  & Soundcloud        & -       \\ \hline
+    3 & Unpopular Youtube & 11274.2 \\ \hline
+      & Popular Youtube   & 9175.0 \\ \hline
+      & Twitch.tv         & 11325.4 \\ \hline
+      & Soundcloud        & 1689.6 \\ \hline
     \end{tabular}}

### 2016-08-28 Writeup/paper.tex
Update the discussion of UCT data to reflect the new values' interesting points

@@
 Being a significantly higher-bandwidth connection than what is available to a home user, this test over UCT's network makes the effects of caching and performance of CDNs more pronounced.
-The Youtube web page  gets served at a much lower ping than the actual content, suggesting that the web page is being cached within UCT's network.
-Also note the difference in throughput for the unpopular Youtube video on the first run to the other runs.
-On run 1 the video is not cached (as is evident by the higher ping) and is delivered at a far lower throughput than on subsequent or than the popular Youtube video.
+Note the difference in throughput for the unpopular Youtube video on the first run to the second and third runs.
+On run 1 the video is not cached (as is evident by the higher ping) and is delivered at a bitrate far below what the connection supports.
+On the run 2 the video has been cached and is delivered with a significantly higher throughput.
+What is interesting to note however, is that on run 3 the throughput is again significantly higher than run 2, even though the ping to the server that delivers it has not changed.
+This suggests that the cache considers it to be "hotter" because of the additional request for it, and serves it at a higher throughput.
 
-Another point of particular interest is the very low ping and hop counts that appear in test case 2.
-The results show the test machine's IP as the IP that the content was being retrieved from.
-This is most likely a bug in our tool's parsing of tcpdump's output.
+Another interesting point to make is that the throughput recorded for Twitch.tv is actually significantly higher than that of Youtube, even for very popular videos.
+This is surprising since the Twitch.tv content is not being delivered from a server residing on the African continent, while the popular Youtube content is being delivered from caches within Cape Town.
 

### 2016-08-28 Writeup/paper.tex
Clean up some TODOs

@@
 \subsection{Home network}
-%TODO (Jacques) I think it might be good to analyse the WHOIS organisation for Twitch and Soundcloud.
-Is the same organisation serving up the content for each ISP?
-Who is serving up the content for these two services?
-
 % TODO (Brian) Maybe run a speed test so we can quote the results and give perspective for our result numbers?
@@
 \end{table}
-% TODO: Table of "offset from median" of the metrics for each ISP
 It is immediately clear that the throughput does not differ much across websites or runs, although this is not unexpected given the relatively low bandwidth of the home connection.
@@
 \end{table}
-While the different ISPs clearly perform differently, the only significant trend is that WebAfrica consistently gave a higher ping, although still less than 100ms, suggesting that the caches for WebAfrica are still within South Africa but not in Cape Town (for example, they could be in Johannesburg).
-% Can you expand the above statement. What is less than 100ms? Because twitch and soundcloud is always in EU > 100ms.
+While the different ISPs clearly perform differently, the only significant trend is that WebAfrica consistently gave a higher ping than other ISPs.
+The only exception to this is the ping to the Youtube website where WebAfrica performed slightly better than the median.
+
 The differences in throughput are not significant and while there are some significant differences in latency, they are not consistent and so are likely due to external factors on the network.

### 2016-08-28 Writeup/paper.tex
Minor improvements to related work section

@@
 Casas \textit{et al.} \cite{6975242} took an ISP traffic view by analysing 1 months worth of YouTube packet flows from a large European ISP.
-The study challenges Google's Video Quality Report \footnote{http://www.google.com/get/videoqualityreport/} as it only considers ISP and access link bottlenecks as the root cause of bad user experience \cite{6975242}.
+The study challenges Google's Video Quality Report\footnote{http://www.google.com/get/videoqualityreport/} as it only considers ISP and access link bottlenecks as the root cause of bad user experience \cite{6975242}.
 Casas \textit{et al.} \cite{6975242} presents how poor content server selection by Google resulted in a large scale reduction for in QoE for many YouTube users.
 Fiadino \textit{et al.} \cite{6932930} developed an tool for ISP's to detect unexpected cache-selection events and changes in the traffic delivered by CDNs.
-As such, anomalous CDN behaviour can have a large impact for ISP's carrying the traffic and end-users \cite{6932930, Plissonneau:2012:LVH:2155555.2155588}.
+Anomalous CDN behaviour has been shown to have a large impact for ISP's carrying the traffic and end-users \cite{6932930, Plissonneau:2012:LVH:2155555.2155588}.
 Zhu \textit{et al.} \cite{6233056} developed LatLong, a tool for CDN's to diagnose large latency increases on the network through passive measurement of traffic and routing.
 Results from analysing a one month's data from Google's CDN show that more than 40\% of latency increases coincide with interdomain routing changes and more than one-third involve a shift in traffic to different servers.
-Juluri \textit{et al.} \cite{6038496} developed a tool to measure playback quality on an end-host.
-The tool captures various metrics such as delay towards the server, download
-rates, and buffering duration \cite{6038496}. These can then be used to measure Quality of Experience.
+Juluri \textit{et al.} \cite{6038496} developed Pytomo, a tool to measure playback quality on an end-host.
+The tool captures various metrics such as delay towards the server, download rates and buffering duration \cite{6038496}.
+These can then be used to measure Quality of Experience.
 
 In 2007 Gill \textit{et al.} \cite{Gill:2007:YTC:1298306.1298310} studied the usage patterns, file properties, popularity and transfer behaviour of YouTube.
-Its findings found that caching could be used effectively to scale Web 2.0 applications such as YouTube \cite{Gill:2007:YTC:1298306.1298310}.In 2011, Torres \textit{et al.} \cite{5961681} analysed a week-long dataset collected from the edge of five networks.
+Its findings found that caching could be used effectively to scale Web 2.0 applications such as YouTube \cite{Gill:2007:YTC:1298306.1298310}.
+In 2011, Torres \textit{et al.} \cite{5961681} analysed a week-long dataset collected from the edge of five networks.
 The study determined the location of YouTube servers and revealed that round trip time (RTT) is not the only factor determining video server selection \cite{5961681}.
@@
 Labovitz \textit{et al.} \cite{Labovitz:2010:IIT:2043164.1851194} analysed 2 years worth of internet traffic through 110 different cable operators, international transit backbones, regional networks and content providers.
-The study found that there was a significant rise in video traffic and that the majority of inter-domain traffic flows directly between large content providers, CDNs and consumer networks.
+The study found that there was a significant rise in video traffic \cite{Labovitz:2010:IIT:2043164.1851194}.
+It also found that the majority of inter-domain traffic flows between large content providers, CDNs and consumer networks \cite{Labovitz:2010:IIT:2043164.1851194}.
 
@@
 \subsection{Home network}
+%TODO (Jacques) I think it might be good to analyse the WHOIS organisation for Twitch and Soundcloud.
+Is the same organisation serving up the content for each ISP?
+Who is serving up the content for these two services?
+
 % TODO (Brian) Maybe run a speed test so we can quote the results and give perspective for our result numbers?
@@
 \end{table}
+% TODO: Table of "offset from median" of the metrics for each ISP
 It is immediately clear that the throughput does not differ much across websites or runs, although this is not unexpected given the relatively low bandwidth of the home connection.
@@
 \end{table}
-While the different ISPs clearly perform differently, the only significant trend is that WebAfrica consistently gave a higher ping than other ISPs.
-The only exception to this is the ping to the Youtube website where WebAfrica performed slightly better than the median.
-
+While the different ISPs clearly perform differently, the only significant trend is that WebAfrica consistently gave a higher ping, although still less than 100ms, suggesting that the caches for WebAfrica are still within South Africa but not in Cape Town (for example, they could be in Johannesburg).
+% Can you expand the above statement. What is less than 100ms? Because twitch and soundcloud is always in EU > 100ms.
 The differences in throughput are not significant and while there are some significant differences in latency, they are not consistent and so are likely due to external factors on the network.
-
-\subsubsection{Content server owners}
-Although not shown in the tables, it is worth noting the results of the WHOIS lookup for the IPs that served the content.
-In the case of Youtube, which server provides the content depends on which networks make use of which local caches as well as whether or not the requested content is available in the cache.
-This is expected as Youtube is a very popular source of content and ISPs setup complex caching systems to reduce bandwidth.
-For Soundcloud and Twitch.tv however, this is not the case.
-All Soundcloud content gets delivered from a IP address that is registered to Amazon, suggesting that Soundcloud uses Amazon Web Services for all of its content storage and distribution.
-The content servers for Twitch.tv are not as consistent.
-While Afrihost, Telkom and WebAfrica all receive Twitch content from an IP registered to ``MCI Communications Services'' (the same company that is the registered owner of the CDN that hosts the content), Axxess and Cybersmart do not.
-Axxess routes to a CDN owned by MCI, but the actual content comes from a server owned by ``Akamai International''.
-Cybersmart does not even receive Twitch content from the same server each time, content arrives from serves that are owned by a variety of other companies.
 
@@
 \begin{itemize}
-	\item Unpopular Youtube video: \\ 
-	https://www.youtube.com/watch?v=yRfwRsJrMzI
-	\item Popular Youtube video: \\
-	https://www.youtube.com/watch?v=9bZkp7q19f0
+	\item Unpopular Youtube video: \\ https://www.youtube.com/watch?v=nKETYT-2NY8
+	\item Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0
 	\item Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release
@@
 	\centering
-    \caption{Ping using UCT network - Test 1}
+	\caption{Ping using UCT network}
 	\label{table:UCTPingTests-TestCase1}
@@
 	Run & Source & Website & CDN & Content \\ \hline
-    1 & Unpopular Youtube & 19  & 18  & 184 \\ \hline
-      & Popular Youtube   & 18  & 18  & 18  \\ \hline
+	1 & Unpopular Youtube & 18  & 49  & 44  \\ \hline
+	  & Popular Youtube   & 45  & 19  & 18  \\ \hline
+	  & Soundcloud        & 179 & 148 & 154 \\ \hline
+	  & Twitch.tv         & 148 & 155 & 148 \\ \hline
+	2 & Unpopular Youtube & 21  & 19  & 19  \\ \hline
+	  & Popular Youtube   & 19  & 26  & 19  \\ \hline
+	  & Soundcloud        & 148 & 149 & 148 \\ \hline
 	  & Twitch.tv         & 148 & 148 & 148 \\ \hline
-      & Soundcloud        & 148 & 149 & 149 \\ \hline
-    2 & Unpopular Youtube & 19  & 18  & 18  \\ \hline
-      & Popular Youtube   & 19  & 18  & 19  \\ \hline
-      & Twitch.tv         & 148 & 150 & 153 \\ \hline
-      & Soundcloud        & 148 & 148 & 192 \\ \hline
-    3 & Unpopular Youtube & 19  & 19  & 18  \\ \hline
-      & Popular Youtube   & 19  & 18  & 18  \\ \hline
-      & Twitch.tv         & 148 & 152 & 148 \\ \hline
-      & Soundcloud        & 148 & 149 & 150 \\ \hline
+	3 & Unpopular Youtube & 3   & 19  & 19  \\ \hline
+	  & Popular Youtube   & 2   & 45  & 68  \\ \hline
+	  & Soundcloud        & 148 & 148 & 148 \\ \hline
+	  & Twitch.tv         & 151 & 154 & 148 \\ \hline
 	\end{tabular}}
@@
 	\centering
-	\caption{Hop count using UCT network - Test 1}
+	\caption{Hop count using UCT network}
 	\label{table:UCTHopCount-TestCase1}
@@
 	Run & Source & Website & CDN & Content \\ \hline
-    1 & Unpopular Youtube & 9 & 9 & 16 \\ \hline
+	1 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
 	  & Popular Youtube   & 9 & 9 & 9 \\ \hline
-      & Twitch.tv         & 13 & 11 & 11 \\ \hline
-      & Soundcloud        & 11 & 18 & 18 \\ \hline
-    2 & Unpopular Youtube & 10 & 9 & 9 \\ \hline
-      & Popular Youtube   & 10 & 9 & 9 \\ \hline
-      & Twitch.tv         & 12 & 13 & 13 \\ \hline
-      & Soundcloud        & 11 & 17 & 17 \\ \hline
-    3 & Unpopular Youtube & 10 & 9 & 9 \\ \hline
+	  & Soundcloud        & 9 & 9 & 9 \\ \hline
+	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
+	2 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
 	  & Popular Youtube   & 9 & 9 & 9 \\ \hline
-      & Twitch.tv         & 13 & 13 & 13 \\ \hline
-      & Soundcloud        & 11 & 18 & 18 \\ \hline
+	  & Soundcloud        & 9 & 9 & 9 \\ \hline
+	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
+	3 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
+	  & Popular Youtube   & 9 & 9 & 9 \\ \hline
+	  & Soundcloud        & 9 & 9 & 9 \\ \hline
+	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
 	\end{tabular}}
@@
 	\centering
-	\caption{Throughput using UCT network - Test 1}
+	\caption{Throughput using UCT network}
 	\label{table:UCTThroughput-TestCase1}
@@
 	Run & Source & Content \\ \hline
-    1 & Unpopular Youtube & 521.5  \\ \hline
-      & Popular Youtube   & 9809.9 \\ \hline
-      & Twitch.tv         & 11366.4    \\ \hline
+	1 & Unpopular Youtube & 1484.8  \\ \hline
+	  & Popular Youtube   & 8560.6  \\ \hline
+	  & Soundcloud        & 1351.7  \\ \hline
+	  & Twitch.tv         & 11284.5 \\ \hline
+	2 & Unpopular Youtube & 7690.2  \\ \hline
+	  & Popular Youtube   & 8161.3  \\ \hline
 	  & Soundcloud        & -       \\ \hline
-    2 & Unpopular Youtube & 6481.9  \\ \hline
-      & Popular Youtube   & 9840.6  \\ \hline
-      & Twitch.tv         & 3440.6    \\ \hline
+	  & Twitch.tv         & 11264.0 \\ \hline
+	3 & Unpopular Youtube & 7598.1  \\ \hline
+	  & Popular Youtube   & 9543.7  \\ \hline
 	  & Soundcloud        & -       \\ \hline  
-    3 & Unpopular Youtube & 8069.1  \\ \hline
-      & Popular Youtube   & 9881.6 \\ \hline
-      & Twitch.tv         & 11335.7    \\ \hline
-      & Soundcloud        & -    \\ \hline
+	  & Twitch.tv         & 11233.3 \\ \hline
 	\end{tabular}}
@@
 \begin{itemize}
-	\item Unpopular Youtube video: \\ 
-	https://www.youtube.com/watch?v=tSzaFuCxjs0
-	\item Popular Youtube video: \\
-	https://www.youtube.com/watch?v=9bZkp7q19f0
+	\item Unpopular Youtube video: \\ https://www.youtube.com/watch?v=nKETYT-2NY8
+	\item Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0
 	\item Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release
@@
 	\centering
-	\caption{Ping using UCT network - Test 2}
+	\caption{Ping using UCT network}
 	\label{table:UCTPing-TestCase2}
@@
 	Run & Source & Website & CDN & Content \\ \hline
-    1 & Unpopular Youtube & 19 & 3 & 182  \\ \hline
-      & Popular Youtube   & 19 & 18 & 18  \\ \hline
-      & Twitch.tv         & 148 & 150 & 148  \\ \hline
+	1 & Unpopular Youtube & 4   & 19  & 188 \\ \hline
+	  & Popular Youtube   & 4   & 19  & 21  \\ \hline
+	  & Twitch.tv         & 148 & 154 & 148 \\ \hline
+	  & Soundcloud        & 148 & 148 & 0   \\ \hline
+	2 & Unpopular Youtube & 3   & 47  & 19  \\ \hline
+	  & Popular Youtube   & 4   & 20  & 19  \\ \hline
+	  & Twitch.tv         & 172 & 154 & 0   \\ \hline
+	  & Soundcloud        & 148 & 149 & 149 \\ \hline
+	3 & Unpopular Youtube & 4   & 33  & 19  \\ \hline
+	  & Popular Youtube   & 3   & 20  & 18  \\ \hline
+	  & Twitch.tv         & 149 & 148 & 0   \\ \hline
 	  & Soundcloud        & 148 & 148 & 148 \\ \hline
-    2 & Unpopular Youtube & 19 & 3 & 3  \\ \hline
-      & Popular Youtube   & 19 & 18 & 18  \\ \hline
-      & Twitch.tv         & 148 & 150 & 150  \\ \hline
-      & Soundcloud        & 148 & 148 & 148  \\ \hline
-    3 & Unpopular Youtube & 19 & 3 & 3  \\ \hline
-      & Popular Youtube   & 20 & 18 & 18 \\ \hline
-      & Twitch.tv         & 148 & 148 & 148  \\ \hline
-      & Soundcloud        & 148 & 149 & 148  \\ \hline
 	\end{tabular}}
@@
 	\centering
-	\caption{Hop count using UCT network - Test 2}
+	\caption{Hop count using UCT network}
 	\label{table:UCTHopCount-TestCase2}
@@
 	\small
+	% TODO: Update these with correct values
 	\begin{tabular}{|l|l|c|c|c|} \hline
 	Run & Source & Website & CDN & Content \\ \hline
-    1 & Unpopular Youtube & 9 & 7 & 16  \\ \hline
-      & Popular Youtube   & 10 & 9 & 9  \\ \hline
-      & Twitch.tv         & 12 & 13 & 13  \\ \hline
-      & Soundcloud        & 11 & 17 & 17  \\ \hline
-    2 & Unpopular Youtube & 10 & 7 & 7  \\ \hline
+	1 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
 	  & Popular Youtube   & 9 & 9 & 9 \\ \hline
-      & Twitch.tv         & 13 & 13 & 13  \\ \hline
-      & Soundcloud        & 11 & 16 & 16  \\ \hline
-    3 & Unpopular Youtube & 10 & 7 & 7  \\ \hline
+	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
+	  & Soundcloud        & 9 & 9 & 1 \\ \hline
+	2 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
 	  & Popular Youtube   & 9 & 9 & 9 \\ \hline
-      & Twitch.tv         & 12 & 12 & 12  \\ \hline
-      & Soundcloud        & 11 & 18 & 18  \\ \hline
+	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
+	  & Soundcloud        & 9 & 9 & 1 \\ \hline
+	3 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
+	  & Popular Youtube   & 9 & 9 & 9 \\ \hline
+	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
+	  & Soundcloud        & 9 & 9 & 1 \\ \hline
 	\end{tabular}}
@@
 	\centering
-	\caption{Throughput using UCT network - Test 2}
+	\caption{Throughput using UCT network}
 	\label{table:UCTThroughput-TestCase2}
@@
 	Run & Source & Content \\ \hline
-    1 & Unpopular Youtube & 1525.8 \\ \hline
-      & Popular Youtube   & 9799.7 \\ \hline
-      & Twitch.tv         & 11427.8 \\ \hline
-      & Soundcloud        & - \\ \hline
-    2 & Unpopular Youtube & 4331.5 \\ \hline
-      & Popular Youtube   & 9820.2 \\ \hline
+	1 & Unpopular Youtube & 190.9   \\ \hline
+	  & Popular Youtube   & 8048.6  \\ \hline
+	  & Twitch.tv         & 10526.7 \\ \hline
+	  & Soundcloud        & 1341.4  \\ \hline
+	2 & Unpopular Youtube & 9513.0  \\ \hline
+	  & Popular Youtube   & 8335.4  \\ \hline
 	  & Twitch.tv         & 11397.1 \\ \hline
 	  & Soundcloud        & -       \\ \hline
-    3 & Unpopular Youtube & 11274.2 \\ \hline
-      & Popular Youtube   & 9175.0 \\ \hline
-      & Twitch.tv         & 11325.4 \\ \hline
-      & Soundcloud        & 1689.6 \\ \hline
+	3 & Unpopular Youtube & 9840.6  \\ \hline
+	  & Popular Youtube   & 7260.2  \\ \hline
+	  & Twitch.tv         & 11274.2 \\ \hline  
+	  & Soundcloud        & -       \\ \hline
 	\end{tabular}}
@@
 Being a significantly higher-bandwidth connection than what is available to a home user, this test over UCT's network makes the effects of caching and performance of CDNs more pronounced.
-Note the difference in throughput for the unpopular Youtube video on the first run to the second and third runs.
-On run 1 the video is not cached (as is evident by the higher ping) and is delivered at a bitrate far below what the connection supports.
-On the run 2 the video has been cached and is delivered with a significantly higher throughput.
-What is interesting to note however, is that on run 3 the throughput is again significantly higher than run 2, even though the ping to the server that delivers it has not changed.
-This suggests that the cache considers it to be "hotter" because of the additional request for it, and serves it at a higher throughput.
+The Youtube web page  gets served at a much lower ping than the actual content, suggesting that the web page is being cached within UCT's network.
+Also note the difference in throughput for the unpopular Youtube video on the first run to the other runs.
+On run 1 the video is not cached (as is evident by the higher ping) and is delivered at a far lower throughput than on subsequent or than the popular Youtube video.
 
-Another interesting point to make is that the throughput recorded for Twitch.tv is actually significantly higher than that of Youtube, even for very popular videos.
-This is surprising since the Twitch.tv content is not being delivered from a server residing on the African continent, while the popular Youtube content is being delivered from caches within Cape Town.
+Another point of particular interest is the very low ping and hop counts that appear in test case 2.
+The results show the test machine's IP as the IP that the content was being retrieved from.
+This is most likely a bug in our tool's parsing of tcpdump's output.
 

### 2016-08-28 Writeup/paper.tex
Expand discussion on slow UCT unpopular YT run 2 Use RTT instead of referring to ping Various grammatical and spelling fixes

@@
 In 2011, Torres \textit{et al.} \cite{5961681} analysed a week-long dataset collected from the edge of five networks.
-The study determined the location of YouTube servers and revealed that round trip time (RTT) is not the only factor determining video server selection \cite{5961681}.
+The study determined the location of YouTube servers and revealed that round-trip time (RTT) is not the only factor determining video server selection \cite{5961681}.
 Other factors that were found to affect server selection were load-balancing, the DNS server used and popularity of the accessed video \cite{5961681}.
@@
 \subsubsection{Results across ISPs}
-Table \ref{table:avgPingAcrossISP}, \ref{table:avgHopsAcrossISP} and \ref{avgThroughputAcrossISP} show the ping, number of hops and throughput averaged across ISPs.
+Table \ref{table:avgPingAcrossISP}, \ref{table:avgHopsAcrossISP} and \ref{avgThroughputAcrossISP} show the RTT, number of hops and throughput averaged across ISPs.
 
 \begin{table}
-	\caption{Averaged ping across ISPs}
+	\caption{Averaged RTT across ISPs (ms)}
 	\label{table:avgPingAcrossISP}
@@
 \begin{table}
-	\caption{Averaged throughput (KB/s) across ISPs}
+	\caption{Averaged throughput across ISPs (KB/s)}
 	\label{avgThroughputAcrossISP}
@@
 It is immediately clear that the throughput does not differ much across websites or runs, although this is not unexpected given the relatively low bandwidth of the home connection.
-Another trend which is immediately clear is the significant difference between ping and number of hops to Youtube and Soundcloud/Twitch.tv.
+Another trend which is immediately clear is the significant difference between RTT and number of hops to Youtube and Soundcloud/Twitch.tv.
 This is simply because Youtube content is cached within South Africa while Twitch.tv and Soundcloud do not, most likely because they are not large enough to be able to afford setting up expensive caches all over the world.
@@
 In runs 2 and 3 the actual content came from the same organisation that hosts the CDN, but in run 1 we see significant increase in latency and note that the content comes from a different organisation.
-The cause of this is clear if we look at Table \ref{table:LatencyToUnpopularYouTubeVideo} and \ref{table:OrgHostingUnpopularYouTubeVideo} which shows the ping to the content IP and the organisation that manages it.
+The cause of this is clear if we look at Table \ref{table:LatencyToUnpopularYouTubeVideo} and \ref{table:OrgHostingUnpopularYouTubeVideo} which shows the RTT to the content IP and the organisation that manages it.
 
 \begin{table}
-	\caption{Latency to unpopular YouTube video}
+	\caption{RTT to unpopular YouTube video (ms)}
 	\label{table:LatencyToUnpopularYouTubeVideo}
@@
 
-One more thing to notice is that in most cases, the ping to the website is higher than to the CDN or the content.
+One more thing to notice is that in most cases, the RTT to the website is higher than to the CDN or the content.
 This is a useful result as it indicates that content delivery networks are providing an optimized means of delivering high-bandwidth content to users.
@@
 \subsubsection{Results across runs}
-To investigate the differences between ISPs, we present below the offset from the median ping and throughput averaged across the 3 runs.
+To investigate the differences between ISPs, we present below the offset from the median RTT and throughput averaged across the 3 runs.
 Table \ref{table:baselineSpeedTests} contains the results from executing a speed test\footnote{Executed at: http://www.speedtest.net} for each ISP.
 This provides some baseline results for each ISP.
-Table \ref{table:OffsetFromMedianPingToWebsite}, \ref{table:OffsetFromMedianPingToCDN} and \ref{table:OffsetFromMedianPingToContent} contain the offset from median ping to website, CDN and content IP from each ISP respectively.
+Table \ref{table:OffsetFromMedianPingToWebsite}, \ref{table:OffsetFromMedianPingToCDN} and \ref{table:OffsetFromMedianPingToContent} contain the offset from median RTT to website, CDN and content IP from each ISP respectively.
 Table \ref{table:OffsetFromMedianThroughput} contains the offset median throughput for each ISP.
@@
 	\begin{tabular}{|l|c|c|c|} \hline
-		ISP & \small{Ping (ms)} & \small{Downstream (KB/s)} & \small{UpStream (KB/s)} \\ \hline
+		ISP & \small{RTT (ms)} & \small{Downstream (KB/s)} & \small{UpStream (KB/s)} \\ \hline
 		Afrihost   & 9   & 220    & 51.25 \\ \hline
@@
 \begin{table}
-	\caption{Offset from median ping to website (ms, lower is better)}
+	\caption{Offset from median RTT to website (ms, lower is better)}
 	\label{table:OffsetFromMedianPingToWebsite}
@@
 \begin{table}
-	\caption{Offset from median ping to CDN (ms, lower is better)}
+	\caption{Offset from median RTT to CDN (ms, lower is better)}
 	\label{table:OffsetFromMedianPingToCDN}
@@
 \begin{table}
-	\caption{Offset from median ping to content (ms, lower is better)}
+	\caption{Offset from median RTT to content (ms, lower is better)}
 	\label{table:OffsetFromMedianPingToContent}
@@
 \end{table}
-While the different ISPs clearly perform differently, the only significant trend is that WebAfrica consistently gave a higher ping than other ISPs.
-The only exception to this is the ping to the Youtube website where WebAfrica performed slightly better than the median.
+While the different ISPs clearly perform differently, the only significant trend is that WebAfrica consistently gave a higher RTT than other ISPs.
+The only exception to this is the RTT to the Youtube website where WebAfrica performed slightly better than the median.
 
@@
 Axxess routes to a CDN owned by MCI, but the actual content comes from a server owned by ``Akamai International''.
-Cybersmart does not even receive Twitch content from the same server each time, content arrives from serves that are owned by a variety of other companies.
+Cybersmart does not even receive Twitch content from the same server each time, content arrives from servers that are owned by a variety of other companies.
 
@@
 \end{itemize}
-Table \ref{table:UCTPingTests-TestCase1}, \ref{table:UCTHopCount-TestCase1} and \ref{table:UCTThroughput-TestCase1} contain the ping, number of hops and throughput for each run of test case 1.
+Table \ref{table:UCTPingTests-TestCase1}, \ref{table:UCTHopCount-TestCase1} and \ref{table:UCTThroughput-TestCase1} contain the RTT, number of hops and throughput for each run of test case 1.
 
@@
     \centering
-    \caption{Ping using UCT network - Test 1}
+    \caption{RTT using UCT network (ms) - Test 1}
     \label{table:UCTPingTests-TestCase1}
@@
 	\centering
-	\caption{Throughput using UCT network - Test 1}
+	\caption{Throughput using UCT network (KB/s) - Test 1}
 	\label{table:UCTThroughput-TestCase1}
@@
     \begin{tabular}{|l|l|c|c|c|} \hline
-    Run & Source & Content    \\ \hline
+    Run & Source & Content (KB/s)    \\ \hline
     1 & Unpopular Youtube & 521.5  \\ \hline
@@
 \end{itemize}
-Table \ref{table:UCTPing-TestCase2}, \ref{table:UCTHopCount-TestCase2} and \ref{table:UCTThroughput-TestCase2} contain the ping, number of hops and throughput for run of test case 2.
+Table \ref{table:UCTPing-TestCase2}, \ref{table:UCTHopCount-TestCase2} and \ref{table:UCTThroughput-TestCase2} contain the RTT, number of hops and throughput for run of test case 2.
 
@@
 	\centering
-	\caption{Ping using UCT network - Test 2}
+	\caption{RTT using UCT network (ms) - Test 2}
 	\label{table:UCTPing-TestCase2}
@@
 	\centering
-	\caption{Throughput using UCT network - Test 2}
+	\caption{Throughput using UCT network (KB/s) - Test 2}
 	\label{table:UCTThroughput-TestCase2}
@@
 Note the difference in throughput for the unpopular Youtube video on the first run to the second and third runs.
-On run 1 the video is not cached (as is evident by the higher ping) and is delivered at a bitrate far below what the connection supports.
+On run 1 the video is not cached (as is evident by the higher RTT) and is delivered at a bitrate far below what the connection supports.
 On the run 2 the video has been cached and is delivered with a significantly higher throughput.
-What is interesting to note however, is that on run 3 the throughput is again significantly higher than run 2, even though the ping to the server that delivers it has not changed.
-This suggests that the cache considers it to be "hotter" because of the additional request for it, and serves it at a higher throughput.
+What is interesting to note however, is that on run 3 the throughput is again significantly higher than run 2, even though the RTT to the server that delivers it has not changed.
+This suggests that the cache considers it to be ``hotter'' because of the additional request for it, and serves it at a higher throughput.
+Another possibility is that while video is available at the server, the caching process has not fully completed, leading to slower throughput on run 2.
+The aforementioned behaviour were found to hold true for subsequent tests on other unpopular YouTube videos, not depicted in this paper.
 

### 2016-08-28 Writeup/paper.tex
Update our method for determining content IP

@@
 
-Next we go through every packet that tcpdump captured and find the IP that sent us the most packets.
-We consider that to be the IP that the content actually came from, as long as more than one third of the captured packets came from that IP.
-In the event that no single IP was the source of more than one third of the captured packets, we retry up to three times.
+Next we go through every packet that tcpdump captured, we discard every packet where the source IP is the local machine's IP.
+Of these filtered packets, we find the IP that sent us the most packets.
+We consider that to be the IP that the content actually came from, as long as more than one half of the filtered packets came from that IP.
+In the event that no single IP was the source of more than a half of the filtered packets, we retry up to three times.
 This retry behaviour gives our test greater stability in the face of existing network traffic.

### 2016-08-28 Writeup/paper.tex
Some minor edits

@@
 With new content constantly getting generated around the world, caching strategies are required so that this content can be served up at a high throughput from as close as possible to the user.
-ISPs play a critical role in this through their peering policies and by providing their own CDNs for various content \cite{Labovitz:2010:IIT:2043164.1851194}.
+Internet Service Providers (ISPs) play a critical role in this through their peering policies and by providing their own CDNs for various content \cite{Labovitz:2010:IIT:2043164.1851194}.
 
 Our aim in this paper is to investigate the performance of the CDN's that serve this content.
-We will examine different streaming services across a variety of South African Internet Service Providers (ISP) to examine how traffic is routed and where it comes from.
+We will examine different streaming services across a variety of South African ISPs to examine how traffic is routed and where it comes from.
 In addition, we will also examine the caching behaviour of YouTube, which has local caches in South Africa.
@@
 Section \ref{sec:method} describes the tool that we developed and details the steps we followed in using it to capture our results.
-Section \ref{sec:results} presents the results and a discussion thereof.
+Section \ref{sec:results} presents the results and discussions thereof.
 
@@
 There have been a number of studies on how the performance of video streaming affects the quality of experience (QoE) for the user.
-Casas \textit{et al.} \cite{6975242} took an ISP traffic view by analysing 1 months worth of YouTube packet flows from a large European ISP.
+Casas \textit{et al.} \cite{6975242} took an ISP traffic view by analysing 1 month's worth of YouTube packet flows from a large European ISP.
 The study challenges Google's Video Quality Report\footnote{http://www.google.com/get/videoqualityreport/} as it only considers ISP and access link bottlenecks as the root cause of bad user experience \cite{6975242}.
 Casas \textit{et al.} \cite{6975242} presents how poor content server selection by Google resulted in a large scale reduction for in QoE for many YouTube users.
-Fiadino \textit{et al.} \cite{6932930} developed an tool for ISP's to detect unexpected cache-selection events and changes in the traffic delivered by CDNs.
-Anomalous CDN behaviour has been shown to have a large impact for ISP's carrying the traffic and end-users \cite{6932930, Plissonneau:2012:LVH:2155555.2155588}.
-Zhu \textit{et al.} \cite{6233056} developed LatLong, a tool for CDN's to diagnose large latency increases on the network through passive measurement of traffic and routing.
+Fiadino \textit{et al.} \cite{6932930} developed a tool for ISPs to detect unexpected cache-selection events and changes in the traffic delivered by CDNs.
+Anomalous CDN behaviour has been shown to have a large impact for ISPs carrying the traffic and end-users \cite{6932930, Plissonneau:2012:LVH:2155555.2155588}.
+Zhu \textit{et al.} \cite{6233056} developed LatLong, a tool for CDNs to diagnose large latency increases on the network through passive measurement of traffic and routing.
 Results from analysing a one month's data from Google's CDN show that more than 40\% of latency increases coincide with interdomain routing changes and more than one-third involve a shift in traffic to different servers.
@@
 We also measure the throughput to the CDN.
-To gain further insight into the potential causes for variances in performance, we also take note of the location and hosting organisation of the web page and CDN IPs.
+To gain further insight into the potential causes for variances in performance, we also take note of the location and hosting organisation of the web page and CDN IPs as well as the IP which the content was actually delivered from.
 The source code for our tool is publicly available on GitHub\footnote{CDNPerf -  https://github.com/jacquesh/cdnperf}.
@@
 Another possibility is that while video is available at the server, the caching process has not fully completed, leading to slower throughput on run 2.
-The aforementioned behaviour were found to hold true for subsequent tests on other unpopular YouTube videos, not depicted in this paper.
+This behaviour was repeated in subsequent tests on other unpopular YouTube videos.
+For brevity we have not included the results of the additional tests in this paper.
 
-Another interesting point to make is that the throughput recorded for Twitch.tv is actually significantly higher than that of Youtube, even for very popular videos.
+Another trend to take note of is that the throughput recorded for Twitch.tv is actually significantly higher than that of Youtube, even for very popular videos.
 This is surprising since the Twitch.tv content is not being delivered from a server residing on the African continent, while the popular Youtube content is being delivered from caches within Cape Town.

### 2016-08-28 Writeup/paper.tex
Edit write-up

@@
 % Relevant work that has been done
-There have been a number of studies on how the performance of video streaming affects the quality of experience (QoE) for the user.
+There have been a number of studies on how the performance of video streaming affects the Quality of Experience (QoE) for the user.
 Casas \textit{et al.} \cite{6975242} took an ISP traffic view by analysing 1 month's worth of YouTube packet flows from a large European ISP.
 The study challenges Google's Video Quality Report\footnote{http://www.google.com/get/videoqualityreport/} as it only considers ISP and access link bottlenecks as the root cause of bad user experience \cite{6975242}.
-Casas \textit{et al.} \cite{6975242} presents how poor content server selection by Google resulted in a large scale reduction for in QoE for many YouTube users.
+Casas \textit{et al.} \cite{6975242} presents how poor content server selection by Google resulted in a large scale reduction in QoE for many YouTube users.
 Fiadino \textit{et al.} \cite{6932930} developed a tool for ISPs to detect unexpected cache-selection events and changes in the traffic delivered by CDNs.
@@
 Zhu \textit{et al.} \cite{6233056} developed LatLong, a tool for CDNs to diagnose large latency increases on the network through passive measurement of traffic and routing.
-Results from analysing a one month's data from Google's CDN show that more than 40\% of latency increases coincide with interdomain routing changes and more than one-third involve a shift in traffic to different servers.
+Results from analysing a one month's data from Google's CDN show that more than 40\% of latency increases coincide with inter-domain routing changes and more than one-third involve a shift in traffic to different servers.
 Juluri \textit{et al.} \cite{6038496} developed Pytomo, a tool to measure playback quality on an end-host.
 The tool captures various metrics such as delay towards the server, download rates and buffering duration \cite{6038496}.
-These can then be used to measure Quality of Experience.
+These can then be used to measure QoE.
 
@@
 Labovitz \textit{et al.} \cite{Labovitz:2010:IIT:2043164.1851194} analysed 2 years worth of internet traffic through 110 different cable operators, international transit backbones, regional networks and content providers.
-The study found that there was a significant rise in video traffic \cite{Labovitz:2010:IIT:2043164.1851194}.
-It also found that the majority of inter-domain traffic flows between large content providers, CDNs and consumer networks \cite{Labovitz:2010:IIT:2043164.1851194}.
+The study found that there was a significant rise in video traffic over the 2 year period \cite{Labovitz:2010:IIT:2043164.1851194}.
+It also found that the majority of inter-domain traffic is between large content providers, CDNs and consumer networks \cite{Labovitz:2010:IIT:2043164.1851194}.
 
@@
 \subsection{Measurement and tools}
-% We should mention that on testing YouTube dl performed the same as streaming through browser.
-%
-
 To measure the performance of CDNs, we have created a tool to automatically capture various quantitative and qualitative performance metrics when given a list of URLs to online video or audio content.
-In order to compare the performance of CDNs to that of the websites that present the content, we measure 2 primary quantitative metrics: Ping or Round-trip-time and the number of hops required to reach the server.
-We also measure the throughput to the CDN.
-To gain further insight into the potential causes for variances in performance, we also take note of the location and hosting organisation of the web page and CDN IPs as well as the IP which the content was actually delivered from.
+In order to compare the performance of CDNs to that of the websites that present the content, we measure 2 primary quantitative metrics: ping or RTT and the number of hops required to reach the server.
+We record measurements using the resolved IP of the input URL (later referred to as ``website''), the IP that the browser is directed to obtain the content from (later referred to as ``CDN'') and the IP of the server that actually served up the multimedia content (later referred to as ``content'').
+We also measure the throughput from the multimedia CDN to end-host.
+To gain further insight into the potential causes for variances in performance, we also take note of the location and hosting organisation for each of the aforementioned IPs.
+Lastly, we record the input URL in our output so that each result can be easily identified and aggregated.
 The source code for our tool is publicly available on GitHub\footnote{CDNPerf -  https://github.com/jacquesh/cdnperf}.
@@
 Our tool is written using Python 3, but makes use of a number of third-party tools and services.
-It makes use of the youtube-dl\footnote{youtube-dl: available at https://rg3.github.io/youtube-dl/} tool to download multimedia content (which is used to measure bandwidth, as detailed below), and uses tcpdump to passively capture network traffic (on Windows we use WinDump which is a Windows port of tcpdump, but for the purposes of this report we will refer to tcpdump).
+It makes use of the youtube-dl\footnote{youtube-dl: available at https://rg3.github.io/youtube-dl/} tool to download multimedia content (which is used to measure bandwidth, as detailed below).
+We examined packet traces and found that youtube-dl exhibited the same behaviour as viewing the content through the browser.
+The tool uses tcpdump to passively capture network traffic (on Windows we use WinDump which is a Windows port of tcpdump, but for the purposes of this report we will refer to tcpdump).
 The ipinfo.io service\footnote{ipinfo: available at http://ipinfo.io/} is used to gather information about the organisation that is hosting the website and CDN IP addresses.
+It is also used to determine the approximate location of each IP.
 
-For each input URL we run youtube-dl and ask that it simply return the URL of the actual content and exit.
+For each input URL we run youtube-dl and ask that it simply return the URL that directs us to the content.
 Both URLs are resolved to IP addresses and stored for later measurement.
@@
 \subsection{Sources of multimedia content}
-As mentioned in Section \ref{sec:intro}, Youtube is one of the most popular video streaming services on the internet.
-Since this is not a study of Youtube specifically, we need to gather data on a number of other multimedia streaming services as well.
+As mentioned in Section \ref{sec:intro}, YouTube is one of the most popular video streaming services on the internet.
+Since this is not a study of YouTube specifically, we need to gather data on a number of other multimedia streaming services as well.
 We decided to also gather data about the popular music sharing service Soundcloud, as well as the popular live video streaming platform Twitch.tv.
-Note that our analysis is restricted to on-demand multimedia streaming and we do not consider the performance of live streaming services on Youtube or Twitch.tv.
+Note that our analysis is restricted to on-demand multimedia streaming and we do not consider the performance of live streaming services on YouTube or Twitch.tv.
 Note also that we did not include Netflix in our evaluation.
@@
 
-Of particular interest is the effect of caching on the performance of Youtube videos.
+Of particular interest is the effect of caching on the performance of YouTube videos.
 It is widely known that there are Google caches in South Africa and that local ISPs have their own caches.
-For this reason we specifically included performance evaluations for Youtube videos that are unpopular or have very few views.
+For this reason we specifically included performance evaluations for YouTube videos that are unpopular or have very few views.
 To find such videos, we manually looked through the ``unknownvideos'' section of Reddit\footnote{``/r/unknownvideos - Watch something new'', available at https://www.reddit.com/r/unknownvideos}.
@@
 \subsection{Measurement Location}
-We measure two different scenarios: Home networks and Institutional networks.
+We measure two different scenarios: home networks and institutional networks.
 In the case of home networks, all our measurements were done from the same location (in order to ensure consistency in our results).
@@
 
-In the case of institutional networks, all our measurements were done while connected to the UCT network.
+In the case of institutional networks, all our measurements were done while connected to the University of Cape Town (UCT) network.
 This test was added in order to compare the results from a home network to what one might get on a network with significantly higher bandwidth.
@@
 \subsection{Home network}
-% TODO (Brian) Maybe run a speed test so we can quote the results and give perspective for our result numbers?
-
-We ran our tests on a single home network, gathering measurements for 5 different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) using the same four media URLs\footnote{Unpopular Youtube video: \\ https://www.youtube.com/watch?v=1-xX7hPxMio}\footnote{Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0}\footnote{Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release}\footnote{Twitch.tv video: \\https://www.twitch.tv/dota2ti/v/83400929} on a 2 megabits per second (Mbps) ADSL line from Telkom.
-The Telkom account is uncapped while the rest of the accounts are capped at 1 gigabyte.
+We ran our tests on a single home network, gathering measurements for 5 different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) using the same four media URLs\footnote{Unpopular YouTube video: \\ https://www.youtube.com/watch?v=1-xX7hPxMio}\footnote{Popular YouTube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0}\footnote{Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release}\footnote{Twitch.tv video: \\https://www.twitch.tv/dota2ti/v/83400929} on a 2 megabits per second (Mbps) ADSL line from Telkom.
+The Telkom ISP account is uncapped while the rest of the ISP accounts are capped at 1 gigabyte.
 
@@
 Table \ref{table:avgPingAcrossISP}, \ref{table:avgHopsAcrossISP} and \ref{avgThroughputAcrossISP} show the RTT, number of hops and throughput averaged across ISPs.
-
 \begin{table}
@@
 	Run & Source & Website & CDN & Content \\ \hline
-	1 & Unpopular Youtube & 39  & 35  & 56  \\ \hline
-	  & Popular Youtube   & 60  & 14  & 14  \\ \hline
+	1 & Unpopular YouTube & 39  & 35  & 56  \\ \hline
+	  & Popular YouTube   & 60  & 14  & 14  \\ \hline
 	  & Soundcloud        & 161 & 162 & 184 \\ \hline
 	  & Twitch.tv         & 198 & 159 & 172 \\ \hline
-	2 & Unpopular Youtube & 45  & 14  & 17  \\ \hline
-	  & Popular Youtube   & 63  & 14  & 31  \\ \hline
+	2 & Unpopular YouTube & 45  & 14  & 17  \\ \hline
+	  & Popular YouTube   & 63  & 14  & 31  \\ \hline
 	  & Soundcloud        & 161 & 160 & 165 \\ \hline
 	  & Twitch.tv         & 193 & 159 & 181 \\ \hline
-	3 & Unpopular Youtube & 31  & 17  & 14  \\ \hline
-	  & Popular Youtube   & 31  & 23  & 18  \\ \hline
+	3 & Unpopular YouTube & 31  & 17  & 14  \\ \hline
+	  & Popular YouTube   & 31  & 23  & 18  \\ \hline
 	  & Soundcloud        & 179 & 171 & 160 \\ \hline
@@
 \end{table}
-
 \begin{table}
@@
 	Run & Source & Website & CDN & Content \\ \hline
-	1 & Unpopular Youtube & 10 & 7  & 10 \\ \hline
-	  & Popular Youtube   & 10 & 8  & 8  \\ \hline
+	1 & Unpopular YouTube & 10 & 7  & 10 \\ \hline
+	  & Popular YouTube   & 10 & 8  & 8  \\ \hline
 	  & Soundcloud        & 13 & 18 & 18 \\ \hline
 	  & Twitch.tv         & 14 & 14 & 15 \\ \hline
-	2 & Unpopular Youtube & 10 & 7  & 7  \\ \hline
-	  & Popular Youtube   & 10 & 8  & 8  \\ \hline
+	2 & Unpopular YouTube & 10 & 7  & 7  \\ \hline
+	  & Popular YouTube   & 10 & 8  & 8  \\ \hline
 	  & Soundcloud        & 13 & 18 & 18 \\ \hline
 	  & Twitch.tv         & 13 & 15 & 12 \\ \hline
-	3 & Unpopular Youtube & 10 & 7  & 7  \\ \hline
-	  & Popular Youtube   & 10 & 8  & 8  \\ \hline
+	3 & Unpopular YouTube & 10 & 7  & 7  \\ \hline
+	  & Popular YouTube   & 10 & 8  & 8  \\ \hline
 	  & Soundcloud        & 13 & 18 & 18 \\ \hline
@@
 	Run & Source & Content \\ \hline
-	1 & Unpopular Youtube & 197.8 \\ \hline
-	  & Popular Youtube   & 202.6 \\ \hline
+	1 & Unpopular YouTube & 197.8 \\ \hline
+	  & Popular YouTube   & 202.6 \\ \hline
 	  & Soundcloud        & 197.9 \\ \hline
 	  & Twitch.tv         & 201.2 \\ \hline
-	2 & Unpopular Youtube & 201.9 \\ \hline
-	  & Popular Youtube   & 197.8 \\ \hline
+	2 & Unpopular YouTube & 201.9 \\ \hline
+	  & Popular YouTube   & 197.8 \\ \hline
 	  & Soundcloud        & 201.3 \\ \hline
 	  & Twitch.tv         & 203.1 \\ \hline
-	3 & Unpopular Youtube & 202.8 \\ \hline
-	  & Popular Youtube   & 200.4 \\ \hline
+	3 & Unpopular YouTube & 202.8 \\ \hline
+	  & Popular YouTube   & 200.4 \\ \hline
 	  & Soundcloud        & 203.6 \\ \hline
@@
 It is immediately clear that the throughput does not differ much across websites or runs, although this is not unexpected given the relatively low bandwidth of the home connection.
-Another trend which is immediately clear is the significant difference between RTT and number of hops to Youtube and Soundcloud/Twitch.tv.
-This is simply because Youtube content is cached within South Africa while Twitch.tv and Soundcloud do not, most likely because they are not large enough to be able to afford setting up expensive caches all over the world.
+Another trend which is immediately clear is the significant difference between RTT and number of hops to YouTube and Soundcloud/Twitch.tv.
+This is simply because YouTube content is cached within South Africa while Twitch.tv and Soundcloud do not, most likely because they are not large enough to be able to afford setting up expensive caches all over the world.
 
-One thing that is less obvious is the difference of the first run to the other two for the unpopular Youtube video.
+One thing that is less obvious is the difference of the first run to the other two for the unpopular YouTube video.
 In runs 2 and 3 the actual content came from the same organisation that hosts the CDN, but in run 1 we see significant increase in latency and note that the content comes from a different organisation.
@@
 \subsubsection{Results across runs}
-To investigate the differences between ISPs, we present below the offset from the median RTT and throughput averaged across the 3 runs.
+To investigate the differences between ISPs, we present the offset from the median RTT and throughput averaged across the 3 runs.
 Table \ref{table:baselineSpeedTests} contains the results from executing a speed test\footnote{Executed at: http://www.speedtest.net} for each ISP.
@@
 		ISP & \small{RTT (ms)} & \small{Downstream (KB/s)} & \small{UpStream (KB/s)} \\ \hline
-		Afrihost   & 9   & 220    & 51.25 \\ \hline
-		Axxess     & 10  & 221.25 & 55 \\ \hline
-		Cybersmart & 10  & 218.75 & 53.75 \\ \hline
-		Telkom     & 12  & 215    & 43.75 \\ \hline
-		WebAfrica  & 10  & 221.25 & 56.25 \\ \hline
+		Afrihost   & 9   & 215 & 50 \\ \hline
+		Axxess     & 10  & 216 & 54 \\ \hline
+		Cybersmart & 10  & 214 & 52 \\ \hline
+		Telkom     & 12  & 210 & 43 \\ \hline
+		WebAfrica  & 10  & 216 & 55 \\ \hline
 		\textbf{\textit{Average}}  & \textbf{\textit{10.2}}  & \textbf{\textit{219.25}} & \textbf{\textit{52}} \\ \hline
@@
 \end{table}
-While the different ISPs clearly perform differently, the only significant trend is that WebAfrica consistently gave a higher RTT than other ISPs.
-The only exception to this is the RTT to the Youtube website where WebAfrica performed slightly better than the median.
+While each ISP clearly performs differently, the only significant trend is that WebAfrica consistently gave a higher RTT than other ISPs.
+The only exception to this is the RTT to the YouTube website where WebAfrica performed slightly better than the median.
 
@@
 Although not shown in the tables, it is worth noting the results of the WHOIS lookup for the IPs that served the content.
-In the case of Youtube, which server provides the content depends on which networks make use of which local caches as well as whether or not the requested content is available in the cache.
-This is expected as Youtube is a very popular source of content and ISPs setup complex caching systems to reduce bandwidth.
+In the case of YouTube, which server provides the content depends on which networks make use of which local caches as well as whether or not the requested content is available in the cache.
+This is expected as YouTube is a very popular source of content and ISPs setup complex caching systems to reduce bandwidth.
 For Soundcloud and Twitch.tv however, this is not the case.
@@
 \begin{itemize}
-	\item Unpopular Youtube video: \\ 
+	\item Unpopular YouTube video: \\ 
 	https://www.youtube.com/watch?v=yRfwRsJrMzI
-	\item Popular Youtube video: \\
+	\item Popular YouTube video: \\
 	https://www.youtube.com/watch?v=9bZkp7q19f0
@@
     Run & Source & Website & CDN & Content \\ \hline
-    1 & Unpopular Youtube & 19  & 18  & 184 \\ \hline
-      & Popular Youtube   & 18  & 18  & 18  \\ \hline
+    1 & Unpopular YouTube & 19  & 18  & 184 \\ \hline
+      & Popular YouTube   & 18  & 18  & 18  \\ \hline
       & Twitch.tv         & 148 & 148 & 148 \\ \hline
       & Soundcloud        & 148 & 149 & 149 \\ \hline
-    2 & Unpopular Youtube & 19  & 18  & 18  \\ \hline
-      & Popular Youtube   & 19  & 18  & 19  \\ \hline
+    2 & Unpopular YouTube & 19  & 18  & 18  \\ \hline
+      & Popular YouTube   & 19  & 18  & 19  \\ \hline
       & Twitch.tv         & 148 & 150 & 153 \\ \hline
       & Soundcloud        & 148 & 148 & 192 \\ \hline
-    3 & Unpopular Youtube & 19  & 19  & 18  \\ \hline
-      & Popular Youtube   & 19  & 18  & 18  \\ \hline
+    3 & Unpopular YouTube & 19  & 19  & 18  \\ \hline
+      & Popular YouTube   & 19  & 18  & 18  \\ \hline
       & Twitch.tv         & 148 & 152 & 148 \\ \hline
@@
     Run & Source & Website & CDN & Content \\ \hline
-    1 & Unpopular Youtube & 9 & 9 & 16 \\ \hline
-      & Popular Youtube   & 9 & 9 & 9 \\ \hline
+    1 & Unpopular YouTube & 9 & 9 & 16 \\ \hline
+      & Popular YouTube   & 9 & 9 & 9 \\ \hline
       & Twitch.tv         & 13 & 11 & 11 \\ \hline
       & Soundcloud        & 11 & 18 & 18 \\ \hline
-    2 & Unpopular Youtube & 10 & 9 & 9 \\ \hline
-      & Popular Youtube   & 10 & 9 & 9 \\ \hline
+    2 & Unpopular YouTube & 10 & 9 & 9 \\ \hline
+      & Popular YouTube   & 10 & 9 & 9 \\ \hline
       & Twitch.tv         & 12 & 13 & 13 \\ \hline
       & Soundcloud        & 11 & 17 & 17 \\ \hline
-    3 & Unpopular Youtube & 10 & 9 & 9 \\ \hline
-      & Popular Youtube   & 9 & 9 & 9 \\ \hline
+    3 & Unpopular YouTube & 10 & 9 & 9 \\ \hline
+      & Popular YouTube   & 9 & 9 & 9 \\ \hline
       & Twitch.tv         & 13 & 13 & 13 \\ \hline
@@
     Run & Source & Content (KB/s)    \\ \hline
-    1 & Unpopular Youtube & 521.5  \\ \hline
-      & Popular Youtube   & 9809.9 \\ \hline
+    1 & Unpopular YouTube & 521.5  \\ \hline
+      & Popular YouTube   & 9809.9 \\ \hline
       & Twitch.tv         & 11366.4    \\ \hline
       & Soundcloud        & -    \\ \hline
-    2 & Unpopular Youtube & 6481.9  \\ \hline
-      & Popular Youtube   & 9840.6  \\ \hline
+    2 & Unpopular YouTube & 6481.9  \\ \hline
+      & Popular YouTube   & 9840.6  \\ \hline
       & Twitch.tv         & 3440.6    \\ \hline
       & Soundcloud        & -    \\ \hline
-    3 & Unpopular Youtube & 8069.1  \\ \hline
-      & Popular Youtube   & 9881.6 \\ \hline
+    3 & Unpopular YouTube & 8069.1  \\ \hline
+      & Popular YouTube   & 9881.6 \\ \hline
       & Twitch.tv         & 11335.7    \\ \hline
@@
 \begin{itemize}
-	\item Unpopular Youtube video: \\ 
+	\item Unpopular YouTube video: \\ 
 	https://www.youtube.com/watch?v=tSzaFuCxjs0
-	\item Popular Youtube video: \\
+	\item Popular YouTube video: \\
 	https://www.youtube.com/watch?v=9bZkp7q19f0
@@
     Run & Source & Website & CDN & Content \\ \hline
-    1 & Unpopular Youtube & 19 & 3 & 182  \\ \hline
-      & Popular Youtube   & 19 & 18 & 18  \\ \hline
+    1 & Unpopular YouTube & 19 & 3 & 182  \\ \hline
+      & Popular YouTube   & 19 & 18 & 18  \\ \hline
       & Twitch.tv         & 148 & 150 & 148  \\ \hline
       & Soundcloud        & 148 & 148 & 148  \\ \hline
-    2 & Unpopular Youtube & 19 & 3 & 3  \\ \hline
-      & Popular Youtube   & 19 & 18 & 18  \\ \hline
+    2 & Unpopular YouTube & 19 & 3 & 3  \\ \hline
+      & Popular YouTube   & 19 & 18 & 18  \\ \hline
       & Twitch.tv         & 148 & 150 & 150  \\ \hline
       & Soundcloud        & 148 & 148 & 148  \\ \hline
-    3 & Unpopular Youtube & 19 & 3 & 3  \\ \hline
-      & Popular Youtube   & 20 & 18 & 18 \\ \hline
+    3 & Unpopular YouTube & 19 & 3 & 3  \\ \hline
+      & Popular YouTube   & 20 & 18 & 18 \\ \hline
       & Twitch.tv         & 148 & 148 & 148  \\ \hline
@@
     Run & Source & Website & CDN & Content \\ \hline
-    1 & Unpopular Youtube & 9 & 7 & 16  \\ \hline
-      & Popular Youtube   & 10 & 9 & 9  \\ \hline
+    1 & Unpopular YouTube & 9 & 7 & 16  \\ \hline
+      & Popular YouTube   & 10 & 9 & 9  \\ \hline
       & Twitch.tv         & 12 & 13 & 13  \\ \hline
       & Soundcloud        & 11 & 17 & 17  \\ \hline
-    2 & Unpopular Youtube & 10 & 7 & 7  \\ \hline
-      & Popular Youtube   & 9 & 9 & 9  \\ \hline
+    2 & Unpopular YouTube & 10 & 7 & 7  \\ \hline
+      & Popular YouTube   & 9 & 9 & 9  \\ \hline
       & Twitch.tv         & 13 & 13 & 13  \\ \hline
       & Soundcloud        & 11 & 16 & 16  \\ \hline
-    3 & Unpopular Youtube & 10 & 7 & 7  \\ \hline
-      & Popular Youtube   & 9 & 9 & 9  \\ \hline
+    3 & Unpopular YouTube & 10 & 7 & 7  \\ \hline
+      & Popular YouTube   & 9 & 9 & 9  \\ \hline
       & Twitch.tv         & 12 & 12 & 12  \\ \hline
@@
     Run & Source & Content    \\ \hline
-    1 & Unpopular Youtube & 1525.8 \\ \hline
-      & Popular Youtube   & 9799.7 \\ \hline
+    1 & Unpopular YouTube & 1525.8 \\ \hline
+      & Popular YouTube   & 9799.7 \\ \hline
       & Twitch.tv         & 11427.8 \\ \hline
       & Soundcloud        & - \\ \hline
-    2 & Unpopular Youtube & 4331.5 \\ \hline
-      & Popular Youtube   & 9820.2 \\ \hline
+    2 & Unpopular YouTube & 4331.5 \\ \hline
+      & Popular YouTube   & 9820.2 \\ \hline
       & Twitch.tv         & 11397.1 \\ \hline
       & Soundcloud        & - \\ \hline
-    3 & Unpopular Youtube & 11274.2 \\ \hline
-      & Popular Youtube   & 9175.0 \\ \hline
+    3 & Unpopular YouTube & 11274.2 \\ \hline
+      & Popular YouTube   & 9175.0 \\ \hline
       & Twitch.tv         & 11325.4 \\ \hline
@@
 Being a significantly higher-bandwidth connection than what is available to a home user, this test over UCT's network makes the effects of caching and performance of CDNs more pronounced.
-Note the difference in throughput for the unpopular Youtube video on the first run to the second and third runs.
+Note the difference in throughput for the unpopular YouTube video on the first run to the second and third runs.
 On run 1 the video is not cached (as is evident by the higher RTT) and is delivered at a bitrate far below what the connection supports.
@@
 
-Another trend to take note of is that the throughput recorded for Twitch.tv is actually significantly higher than that of Youtube, even for very popular videos.
-This is surprising since the Twitch.tv content is not being delivered from a server residing on the African continent, while the popular Youtube content is being delivered from caches within Cape Town.
+Another trend to take note of is that the throughput recorded for Twitch.tv is actually significantly higher than that of YouTube, even for very popular videos.
+This is surprising since the Twitch.tv content is not being delivered from a server residing on the African continent, while the popular YouTube content is being delivered from caches within Cape Town.
 
 \section{Future Work}\label{sec:futurework}
-Our experiments have focussed on streaming of internet video and audio on-demand, from websites including Youtube, Twitch.tv and Soundcloud.
-In future work we would like to extend this to streaming of live video and audio content such as from Youtube Live or Twitch.tv's live streams.
-Another extension would be to consider the differences in performance of streamed video content to video adverts, which are prevalent both on Youtube and Twitch.tv.
+Our experiments have focussed on streaming of internet video and audio on-demand, from websites including YouTube, Twitch.tv and Soundcloud.
+In future work we would like to extend this to streaming of live video and audio content such as from YouTube Live or Twitch.tv's live streams.
+Another extension would be to consider the differences in performance of streamed video content to video adverts, which are prevalent both on YouTube and Twitch.tv.
 

### 2016-08-28 cdn_perf.py
Force method heading to next page

@@ -10,7 +10,7 @@ from time import sleep
 from datetime import datetime
 
 # Set this to subprocess.DEVNULL for clean output, None for verbose output
-verboseOutputTarget = subprocess.DEVNULL
+verboseOutputTarget = None
 
 # Retry attempts
 numberOfRetries = 3

### 2016-08-28 cdn_perf.py
Move baseline ISP tests Update averages for baseline tests

@@ -10,7 +10,7 @@ from time import sleep
 from datetime import datetime
 
 # Set this to subprocess.DEVNULL for clean output, None for verbose output
-verboseOutputTarget = None
+verboseOutputTarget = subprocess.DEVNULL
 
 # Retry attempts
 numberOfRetries = 3

### 2016-08-28 Writeup/paper.tex
Prevent tables from clipping
Force method heading to next page
Move baseline ISP tests Update averages for baseline tests
Fix spelling error

@@
 It also found that the majority of inter-domain traffic is between large content providers, CDNs and consumer networks \cite{Labovitz:2010:IIT:2043164.1851194}.
-
+\\\\\\
 \section{Method}\label{sec:method}
@@
 The Telkom ISP account is uncapped while the rest of the ISP accounts are capped at 1 gigabyte.
+Table \ref{table:baselineSpeedTests} contains the results from executing a speed test\footnote{Executed at: http://www.speedtest.net} for each ISP.
+This provides some baseline results for each ISP.
+
+\begin{table}
+	\caption{Baseline speed test for each ISP}
+	\label{table:baselineSpeedTests}
+	\makebox[70mm]{
+	\small
+	\begin{tabular}{|l|c|c|c|} \hline
+		ISP & \small{RTT (ms)} & \small{Downstream (KB/s)} & \small{Upstream (KB/s)} \\ \hline
+		Afrihost   & 9   & 215 & 50 \\ \hline
+		Axxess     & 10  & 216 & 54 \\ \hline
+		Cybersmart & 10  & 214 & 52 \\ \hline
+		Telkom     & 12  & 210 & 43 \\ \hline
+		WebAfrica  & 10  & 216 & 55 \\ \hline
+		\textbf{\textit{Average}}  & \textbf{\textit{10.2}}  & \textbf{\textit{214}} & \textbf{\textit{51}} \\ \hline
+	\end{tabular}}
+\end{table}
 
@@
 To investigate the differences between ISPs, we present the offset from the median RTT and throughput averaged across the 3 runs.
-Table \ref{table:baselineSpeedTests} contains the results from executing a speed test\footnote{Executed at: http://www.speedtest.net} for each ISP.
-This provides some baseline results for each ISP.
 Table \ref{table:OffsetFromMedianPingToWebsite}, \ref{table:OffsetFromMedianPingToCDN} and \ref{table:OffsetFromMedianPingToContent} contain the offset from median RTT to website, CDN and content IP from each ISP respectively.
@@
 \begin{table}
-	\caption{Baseline speed test for each ISP}
-	\label{table:baselineSpeedTests}
-	\makebox[75mm]{
-	\small
-	\begin{tabular}{|l|c|c|c|} \hline
-		ISP & \small{RTT (ms)} & \small{Downstream (KB/s)} & \small{UpStream (KB/s)} \\ \hline
-		Afrihost   & 9   & 215 & 50 \\ \hline
-		Axxess     & 10  & 216 & 54 \\ \hline
-		Cybersmart & 10  & 214 & 52 \\ \hline
-		Telkom     & 12  & 210 & 43 \\ \hline
-		WebAfrica  & 10  & 216 & 55 \\ \hline
-		\textbf{\textit{Average}}  & \textbf{\textit{10.2}}  & \textbf{\textit{219.25}} & \textbf{\textit{52}} \\ \hline
-	\end{tabular}}
-\end{table}
-
-\begin{table}
 	\caption{Offset from median RTT to website (ms, lower is better)}
 	\label{table:OffsetFromMedianPingToWebsite}
-	\makebox[75mm]{
+	\makebox[70mm]{
 	\small
@@
 	\label{table:OffsetFromMedianPingToCDN}
-	\makebox[75mm]{
+	\makebox[70mm]{
 	\small
@@
 	\label{table:OffsetFromMedianPingToContent}
-	\makebox[75mm]{
+	\makebox[70mm]{
 	\small
@@
 	\label{table:OffsetFromMedianThroughput}
-	\makebox[75mm]{
+	\makebox[95mm]{
 	\small
@@
 The differences in throughput are not significant and while there are some significant differences in latency, they are not consistent and so are likely due to external factors on the network.
-
+\\\\
 \subsubsection{Content server owners}

### 2016-08-28 Writeup/paper.tex
Add conclusions

@@
 \begin{abstract}
+Modern internet infrastructure consists of deep hierarchies of caches and Content Delivery Networks in order to serve the ever-increasing demand for high-bandwidth multimedia content.
+In this report we present a tool for measuring the impact of Content Delivery Networks on the performance of streaming video and audio content over the internet.
+We analyse the performance impact of these networks from the point of view both of the home user and large-scale institutions.
 \end{abstract}
@@
 The Telkom ISP account is uncapped while the rest of the ISP accounts are capped at 1 gigabyte.
-Table \ref{table:baselineSpeedTests} contains the results from executing a speed test\footnote{Executed at: http://www.speedtest.net} for each ISP.
-This provides some baseline results for each ISP.
-
-\begin{table}
-	\caption{Baseline speed test for each ISP}
-	\label{table:baselineSpeedTests}
-	\makebox[70mm]{
-	\small
-	\begin{tabular}{|l|c|c|c|} \hline
-		ISP & \small{RTT (ms)} & \small{Downstream (KB/s)} & \small{Upstream (KB/s)} \\ \hline
-		Afrihost   & 9   & 215 & 50 \\ \hline
-		Axxess     & 10  & 216 & 54 \\ \hline
-		Cybersmart & 10  & 214 & 52 \\ \hline
-		Telkom     & 12  & 210 & 43 \\ \hline
-		WebAfrica  & 10  & 216 & 55 \\ \hline
-		\textbf{\textit{Average}}  & \textbf{\textit{10.2}}  & \textbf{\textit{214}} & \textbf{\textit{51}} \\ \hline
-	\end{tabular}}
-\end{table}
 
@@
 The differences in throughput are not significant and while there are some significant differences in latency, they are not consistent and so are likely due to external factors on the network.
-\\\\
+
 \subsubsection{Content server owners}
@@
 
+\section{Conclusions}
+We have developed a tool which can take a list of URLs to a range of multimedia services.
+It captures a wide range of quantitative metrics such as: RTT, number of hops required to reach the IP, approximate location of IP and organisation hosting IP.
+Each of the aforementioned metrics are recorded for the resolved IP of the input URL, the IP that the browser is directed to obtain the content from and the IP of the server that actually served up the multimedia content.
+We also measure the throughput from the multimedia CDN to end-host.
+
+We tested from a number of ISPs on a home network as well as an institutional network.
+Our results gained insights on the caching behaviour of YouTube with respect to videos with very few views.
+We found that the majority of unpopular videos are not cached within South Africa.
+The video has to be obtained from a Google cache in Europe.
+We found that after viewing the unpopular video it would be cached on both on the ISP's server and Google's South African cache.
+Subsequent views from the same ISP would come from the ISP cache and views from another ISP would come from Google's South African cache instead of from Europe.
+
+On the institutional network we found that even though, on run 2, the unpopular YouTube video was obtained from the institution's cache, it would always be slower than run 3.
+It was reasoned that this could be because the cache considers it to be ``hotter'' because of the additional request for it, and serves it at a higher throughput.
+Another possibility is that while the video is available at the server, the caching process has not fully completed, leading to slower throughput on run 2.
+
 \small

### 2016-08-28 Writeup/paper.tex
Add an abstract

--- 2016-08-28 Writeup/paper.tex
@@
 % Relevant work that has been done
-There have been a number of studies on how the performance of video streaming affects the Quality of Experience (QoE) for the user.
+There have been a number of studies on how the performance of video streaming affects the quality of experience (QoE) for the user.
 Casas \textit{et al.} \cite{6975242} took an ISP traffic view by analysing 1 month's worth of YouTube packet flows from a large European ISP.
 The study challenges Google's Video Quality Report\footnote{http://www.google.com/get/videoqualityreport/} as it only considers ISP and access link bottlenecks as the root cause of bad user experience \cite{6975242}.
-Casas \textit{et al.} \cite{6975242} presents how poor content server selection by Google resulted in a large scale reduction in QoE for many YouTube users.
+Casas \textit{et al.} \cite{6975242} presents how poor content server selection by Google resulted in a large scale reduction for in QoE for many YouTube users.
 Fiadino \textit{et al.} \cite{6932930} developed a tool for ISPs to detect unexpected cache-selection events and changes in the traffic delivered by CDNs.
@@
 Zhu \textit{et al.} \cite{6233056} developed LatLong, a tool for CDNs to diagnose large latency increases on the network through passive measurement of traffic and routing.
-Results from analysing a one month's data from Google's CDN show that more than 40\% of latency increases coincide with inter-domain routing changes and more than one-third involve a shift in traffic to different servers.
+Results from analysing a one month's data from Google's CDN show that more than 40\% of latency increases coincide with interdomain routing changes and more than one-third involve a shift in traffic to different servers.
 Juluri \textit{et al.} \cite{6038496} developed Pytomo, a tool to measure playback quality on an end-host.
 The tool captures various metrics such as delay towards the server, download rates and buffering duration \cite{6038496}.
-These can then be used to measure QoE.
+These can then be used to measure Quality of Experience.
 
@@
 Labovitz \textit{et al.} \cite{Labovitz:2010:IIT:2043164.1851194} analysed 2 years worth of internet traffic through 110 different cable operators, international transit backbones, regional networks and content providers.
-The study found that there was a significant rise in video traffic over the 2 year period \cite{Labovitz:2010:IIT:2043164.1851194}.
-It also found that the majority of inter-domain traffic is between large content providers, CDNs and consumer networks \cite{Labovitz:2010:IIT:2043164.1851194}.
+The study found that there was a significant rise in video traffic \cite{Labovitz:2010:IIT:2043164.1851194}.
+It also found that the majority of inter-domain traffic flows between large content providers, CDNs and consumer networks \cite{Labovitz:2010:IIT:2043164.1851194}.
 
@@
 \subsection{Measurement and tools}
+% We should mention that on testing YouTube dl performed the same as streaming through browser.
+%
+
 To measure the performance of CDNs, we have created a tool to automatically capture various quantitative and qualitative performance metrics when given a list of URLs to online video or audio content.
-In order to compare the performance of CDNs to that of the websites that present the content, we measure 2 primary quantitative metrics: ping or RTT and the number of hops required to reach the server.
-We record measurements using the resolved IP of the input URL (later referred to as ``website''), the IP that the browser is directed to obtain the content from (later referred to as ``CDN'') and the IP of the server that actually served up the multimedia content (later referred to as ``content'').
-We also measure the throughput from the multimedia CDN to end-host.
-To gain further insight into the potential causes for variances in performance, we also take note of the location and hosting organisation for each of the aforementioned IPs.
-Lastly, we record the input URL in our output so that each result can be easily identified and aggregated.
+In order to compare the performance of CDNs to that of the websites that present the content, we measure 2 primary quantitative metrics: Ping or Round-trip-time and the number of hops required to reach the server.
+We also measure the throughput to the CDN.
+To gain further insight into the potential causes for variances in performance, we also take note of the location and hosting organisation of the web page and CDN IPs as well as the IP which the content was actually delivered from.
 The source code for our tool is publicly available on GitHub\footnote{CDNPerf -  https://github.com/jacquesh/cdnperf}.
@@
 Our tool is written using Python 3, but makes use of a number of third-party tools and services.
-It makes use of the youtube-dl\footnote{youtube-dl: available at https://rg3.github.io/youtube-dl/} tool to download multimedia content (which is used to measure bandwidth, as detailed below).
-We examined packet traces and found that youtube-dl exhibited the same behaviour as viewing the content through the browser.
-The tool uses tcpdump to passively capture network traffic (on Windows we use WinDump which is a Windows port of tcpdump, but for the purposes of this report we will refer to tcpdump).
+It makes use of the youtube-dl\footnote{youtube-dl: available at https://rg3.github.io/youtube-dl/} tool to download multimedia content (which is used to measure bandwidth, as detailed below), and uses tcpdump to passively capture network traffic (on Windows we use WinDump which is a Windows port of tcpdump, but for the purposes of this report we will refer to tcpdump).
 The ipinfo.io service\footnote{ipinfo: available at http://ipinfo.io/} is used to gather information about the organisation that is hosting the website and CDN IP addresses.
-It is also used to determine the approximate location of each IP.
 
-For each input URL we run youtube-dl and ask that it simply return the URL that directs us to the content.
+For each input URL we run youtube-dl and ask that it simply return the URL of the actual content and exit.
 Both URLs are resolved to IP addresses and stored for later measurement.
@@
 \subsection{Sources of multimedia content}
-As mentioned in Section \ref{sec:intro}, YouTube is one of the most popular video streaming services on the internet.
-Since this is not a study of YouTube specifically, we need to gather data on a number of other multimedia streaming services as well.
+As mentioned in Section \ref{sec:intro}, Youtube is one of the most popular video streaming services on the internet.
+Since this is not a study of Youtube specifically, we need to gather data on a number of other multimedia streaming services as well.
 We decided to also gather data about the popular music sharing service Soundcloud, as well as the popular live video streaming platform Twitch.tv.
-Note that our analysis is restricted to on-demand multimedia streaming and we do not consider the performance of live streaming services on YouTube or Twitch.tv.
+Note that our analysis is restricted to on-demand multimedia streaming and we do not consider the performance of live streaming services on Youtube or Twitch.tv.
 Note also that we did not include Netflix in our evaluation.
@@
 
-Of particular interest is the effect of caching on the performance of YouTube videos.
+Of particular interest is the effect of caching on the performance of Youtube videos.
 It is widely known that there are Google caches in South Africa and that local ISPs have their own caches.
-For this reason we specifically included performance evaluations for YouTube videos that are unpopular or have very few views.
+For this reason we specifically included performance evaluations for Youtube videos that are unpopular or have very few views.
 To find such videos, we manually looked through the ``unknownvideos'' section of Reddit\footnote{``/r/unknownvideos - Watch something new'', available at https://www.reddit.com/r/unknownvideos}.
@@
 \subsection{Measurement Location}
-We measure two different scenarios: home networks and institutional networks.
+We measure two different scenarios: Home networks and Institutional networks.
 In the case of home networks, all our measurements were done from the same location (in order to ensure consistency in our results).
@@
 
-In the case of institutional networks, all our measurements were done while connected to the University of Cape Town (UCT) network.
+In the case of institutional networks, all our measurements were done while connected to the UCT network.
 This test was added in order to compare the results from a home network to what one might get on a network with significantly higher bandwidth.
@@
 \subsection{Home network}
-We ran our tests on a single home network, gathering measurements for 5 different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) using the same four media URLs\footnote{Unpopular YouTube video: \\ https://www.youtube.com/watch?v=1-xX7hPxMio}\footnote{Popular YouTube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0}\footnote{Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release}\footnote{Twitch.tv video: \\https://www.twitch.tv/dota2ti/v/83400929} on a 2 megabits per second (Mbps) ADSL line from Telkom.
-The Telkom ISP account is uncapped while the rest of the ISP accounts are capped at 1 gigabyte.
+% TODO (Brian) Maybe run a speed test so we can quote the results and give perspective for our result numbers?
+
+We ran our tests on a single home network, gathering measurements for 5 different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) using the same four media URLs\footnote{Unpopular Youtube video: \\ https://www.youtube.com/watch?v=1-xX7hPxMio}\footnote{Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0}\footnote{Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release}\footnote{Twitch.tv video: \\https://www.twitch.tv/dota2ti/v/83400929} on a 2 megabits per second (Mbps) ADSL line from Telkom.
+The Telkom account is uncapped while the rest of the accounts are capped at 1 gigabyte.
 
@@
 Table \ref{table:avgPingAcrossISP}, \ref{table:avgHopsAcrossISP} and \ref{avgThroughputAcrossISP} show the RTT, number of hops and throughput averaged across ISPs.
+
 \begin{table}
@@
 	Run & Source & Website & CDN & Content \\ \hline
-	1 & Unpopular YouTube & 39  & 35  & 56  \\ \hline
-	  & Popular YouTube   & 60  & 14  & 14  \\ \hline
+	1 & Unpopular Youtube & 39  & 35  & 56  \\ \hline
+	  & Popular Youtube   & 60  & 14  & 14  \\ \hline
 	  & Soundcloud        & 161 & 162 & 184 \\ \hline
 	  & Twitch.tv         & 198 & 159 & 172 \\ \hline
-	2 & Unpopular YouTube & 45  & 14  & 17  \\ \hline
-	  & Popular YouTube   & 63  & 14  & 31  \\ \hline
+	2 & Unpopular Youtube & 45  & 14  & 17  \\ \hline
+	  & Popular Youtube   & 63  & 14  & 31  \\ \hline
 	  & Soundcloud        & 161 & 160 & 165 \\ \hline
 	  & Twitch.tv         & 193 & 159 & 181 \\ \hline
-	3 & Unpopular YouTube & 31  & 17  & 14  \\ \hline
-	  & Popular YouTube   & 31  & 23  & 18  \\ \hline
+	3 & Unpopular Youtube & 31  & 17  & 14  \\ \hline
+	  & Popular Youtube   & 31  & 23  & 18  \\ \hline
 	  & Soundcloud        & 179 & 171 & 160 \\ \hline
@@
 \end{table}
+
 \begin{table}
@@
 	Run & Source & Website & CDN & Content \\ \hline
-	1 & Unpopular YouTube & 10 & 7  & 10 \\ \hline
-	  & Popular YouTube   & 10 & 8  & 8  \\ \hline
+	1 & Unpopular Youtube & 10 & 7  & 10 \\ \hline
+	  & Popular Youtube   & 10 & 8  & 8  \\ \hline
 	  & Soundcloud        & 13 & 18 & 18 \\ \hline
 	  & Twitch.tv         & 14 & 14 & 15 \\ \hline
-	2 & Unpopular YouTube & 10 & 7  & 7  \\ \hline
-	  & Popular YouTube   & 10 & 8  & 8  \\ \hline
+	2 & Unpopular Youtube & 10 & 7  & 7  \\ \hline
+	  & Popular Youtube   & 10 & 8  & 8  \\ \hline
 	  & Soundcloud        & 13 & 18 & 18 \\ \hline
 	  & Twitch.tv         & 13 & 15 & 12 \\ \hline
-	3 & Unpopular YouTube & 10 & 7  & 7  \\ \hline
-	  & Popular YouTube   & 10 & 8  & 8  \\ \hline
+	3 & Unpopular Youtube & 10 & 7  & 7  \\ \hline
+	  & Popular Youtube   & 10 & 8  & 8  \\ \hline
 	  & Soundcloud        & 13 & 18 & 18 \\ \hline
@@
 	Run & Source & Content \\ \hline
-	1 & Unpopular YouTube & 197.8 \\ \hline
-	  & Popular YouTube   & 202.6 \\ \hline
+	1 & Unpopular Youtube & 197.8 \\ \hline
+	  & Popular Youtube   & 202.6 \\ \hline
 	  & Soundcloud        & 197.9 \\ \hline
 	  & Twitch.tv         & 201.2 \\ \hline
-	2 & Unpopular YouTube & 201.9 \\ \hline
-	  & Popular YouTube   & 197.8 \\ \hline
+	2 & Unpopular Youtube & 201.9 \\ \hline
+	  & Popular Youtube   & 197.8 \\ \hline
 	  & Soundcloud        & 201.3 \\ \hline
 	  & Twitch.tv         & 203.1 \\ \hline
-	3 & Unpopular YouTube & 202.8 \\ \hline
-	  & Popular YouTube   & 200.4 \\ \hline
+	3 & Unpopular Youtube & 202.8 \\ \hline
+	  & Popular Youtube   & 200.4 \\ \hline
 	  & Soundcloud        & 203.6 \\ \hline
@@
 It is immediately clear that the throughput does not differ much across websites or runs, although this is not unexpected given the relatively low bandwidth of the home connection.
-Another trend which is immediately clear is the significant difference between RTT and number of hops to YouTube and Soundcloud/Twitch.tv.
-This is simply because YouTube content is cached within South Africa while Twitch.tv and Soundcloud do not, most likely because they are not large enough to be able to afford setting up expensive caches all over the world.
+Another trend which is immediately clear is the significant difference between RTT and number of hops to Youtube and Soundcloud/Twitch.tv.
+This is simply because Youtube content is cached within South Africa while Twitch.tv and Soundcloud do not, most likely because they are not large enough to be able to afford setting up expensive caches all over the world.
 
-One thing that is less obvious is the difference of the first run to the other two for the unpopular YouTube video.
+One thing that is less obvious is the difference of the first run to the other two for the unpopular Youtube video.
 In runs 2 and 3 the actual content came from the same organisation that hosts the CDN, but in run 1 we see significant increase in latency and note that the content comes from a different organisation.
@@
 \subsubsection{Results across runs}
-To investigate the differences between ISPs, we present the offset from the median RTT and throughput averaged across the 3 runs.
+To investigate the differences between ISPs, we present below the offset from the median RTT and throughput averaged across the 3 runs.
 Table \ref{table:baselineSpeedTests} contains the results from executing a speed test\footnote{Executed at: http://www.speedtest.net} for each ISP.
@@
 		ISP & \small{RTT (ms)} & \small{Downstream (KB/s)} & \small{UpStream (KB/s)} \\ \hline
-		Afrihost   & 9   & 215 & 50 \\ \hline
-		Axxess     & 10  & 216 & 54 \\ \hline
-		Cybersmart & 10  & 214 & 52 \\ \hline
-		Telkom     & 12  & 210 & 43 \\ \hline
-		WebAfrica  & 10  & 216 & 55 \\ \hline
+		Afrihost   & 9   & 220    & 51.25 \\ \hline
+		Axxess     & 10  & 221.25 & 55 \\ \hline
+		Cybersmart & 10  & 218.75 & 53.75 \\ \hline
+		Telkom     & 12  & 215    & 43.75 \\ \hline
+		WebAfrica  & 10  & 221.25 & 56.25 \\ \hline
 		\textbf{\textit{Average}}  & \textbf{\textit{10.2}}  & \textbf{\textit{219.25}} & \textbf{\textit{52}} \\ \hline
@@
 \end{table}
-While each ISP clearly performs differently, the only significant trend is that WebAfrica consistently gave a higher RTT than other ISPs.
-The only exception to this is the RTT to the YouTube website where WebAfrica performed slightly better than the median.
+While the different ISPs clearly perform differently, the only significant trend is that WebAfrica consistently gave a higher RTT than other ISPs.
+The only exception to this is the RTT to the Youtube website where WebAfrica performed slightly better than the median.
 
@@
 Although not shown in the tables, it is worth noting the results of the WHOIS lookup for the IPs that served the content.
-In the case of YouTube, which server provides the content depends on which networks make use of which local caches as well as whether or not the requested content is available in the cache.
-This is expected as YouTube is a very popular source of content and ISPs setup complex caching systems to reduce bandwidth.
+In the case of Youtube, which server provides the content depends on which networks make use of which local caches as well as whether or not the requested content is available in the cache.
+This is expected as Youtube is a very popular source of content and ISPs setup complex caching systems to reduce bandwidth.
 For Soundcloud and Twitch.tv however, this is not the case.
@@
 \begin{itemize}
-	\item Unpopular YouTube video: \\ 
+	\item Unpopular Youtube video: \\ 
 	https://www.youtube.com/watch?v=yRfwRsJrMzI
-	\item Popular YouTube video: \\
+	\item Popular Youtube video: \\
 	https://www.youtube.com/watch?v=9bZkp7q19f0
@@
     Run & Source & Website & CDN & Content \\ \hline
-    1 & Unpopular YouTube & 19  & 18  & 184 \\ \hline
-      & Popular YouTube   & 18  & 18  & 18  \\ \hline
+    1 & Unpopular Youtube & 19  & 18  & 184 \\ \hline
+      & Popular Youtube   & 18  & 18  & 18  \\ \hline
       & Twitch.tv         & 148 & 148 & 148 \\ \hline
       & Soundcloud        & 148 & 149 & 149 \\ \hline
-    2 & Unpopular YouTube & 19  & 18  & 18  \\ \hline
-      & Popular YouTube   & 19  & 18  & 19  \\ \hline
+    2 & Unpopular Youtube & 19  & 18  & 18  \\ \hline
+      & Popular Youtube   & 19  & 18  & 19  \\ \hline
       & Twitch.tv         & 148 & 150 & 153 \\ \hline
       & Soundcloud        & 148 & 148 & 192 \\ \hline
-    3 & Unpopular YouTube & 19  & 19  & 18  \\ \hline
-      & Popular YouTube   & 19  & 18  & 18  \\ \hline
+    3 & Unpopular Youtube & 19  & 19  & 18  \\ \hline
+      & Popular Youtube   & 19  & 18  & 18  \\ \hline
       & Twitch.tv         & 148 & 152 & 148 \\ \hline
@@
     Run & Source & Website & CDN & Content \\ \hline
-    1 & Unpopular YouTube & 9 & 9 & 16 \\ \hline
-      & Popular YouTube   & 9 & 9 & 9 \\ \hline
+    1 & Unpopular Youtube & 9 & 9 & 16 \\ \hline
+      & Popular Youtube   & 9 & 9 & 9 \\ \hline
       & Twitch.tv         & 13 & 11 & 11 \\ \hline
       & Soundcloud        & 11 & 18 & 18 \\ \hline
-    2 & Unpopular YouTube & 10 & 9 & 9 \\ \hline
-      & Popular YouTube   & 10 & 9 & 9 \\ \hline
+    2 & Unpopular Youtube & 10 & 9 & 9 \\ \hline
+      & Popular Youtube   & 10 & 9 & 9 \\ \hline
       & Twitch.tv         & 12 & 13 & 13 \\ \hline
       & Soundcloud        & 11 & 17 & 17 \\ \hline
-    3 & Unpopular YouTube & 10 & 9 & 9 \\ \hline
-      & Popular YouTube   & 9 & 9 & 9 \\ \hline
+    3 & Unpopular Youtube & 10 & 9 & 9 \\ \hline
+      & Popular Youtube   & 9 & 9 & 9 \\ \hline
       & Twitch.tv         & 13 & 13 & 13 \\ \hline
@@
     Run & Source & Content (KB/s)    \\ \hline
-    1 & Unpopular YouTube & 521.5  \\ \hline
-      & Popular YouTube   & 9809.9 \\ \hline
+    1 & Unpopular Youtube & 521.5  \\ \hline
+      & Popular Youtube   & 9809.9 \\ \hline
       & Twitch.tv         & 11366.4    \\ \hline
       & Soundcloud        & -    \\ \hline
-    2 & Unpopular YouTube & 6481.9  \\ \hline
-      & Popular YouTube   & 9840.6  \\ \hline
+    2 & Unpopular Youtube & 6481.9  \\ \hline
+      & Popular Youtube   & 9840.6  \\ \hline
       & Twitch.tv         & 3440.6    \\ \hline
       & Soundcloud        & -    \\ \hline
-    3 & Unpopular YouTube & 8069.1  \\ \hline
-      & Popular YouTube   & 9881.6 \\ \hline
+    3 & Unpopular Youtube & 8069.1  \\ \hline
+      & Popular Youtube   & 9881.6 \\ \hline
       & Twitch.tv         & 11335.7    \\ \hline
@@
 \begin{itemize}
-	\item Unpopular YouTube video: \\ 
+	\item Unpopular Youtube video: \\ 
 	https://www.youtube.com/watch?v=tSzaFuCxjs0
-	\item Popular YouTube video: \\
+	\item Popular Youtube video: \\
 	https://www.youtube.com/watch?v=9bZkp7q19f0
@@
     Run & Source & Website & CDN & Content \\ \hline
-    1 & Unpopular YouTube & 19 & 3 & 182  \\ \hline
-      & Popular YouTube   & 19 & 18 & 18  \\ \hline
+    1 & Unpopular Youtube & 19 & 3 & 182  \\ \hline
+      & Popular Youtube   & 19 & 18 & 18  \\ \hline
       & Twitch.tv         & 148 & 150 & 148  \\ \hline
       & Soundcloud        & 148 & 148 & 148  \\ \hline
-    2 & Unpopular YouTube & 19 & 3 & 3  \\ \hline
-      & Popular YouTube   & 19 & 18 & 18  \\ \hline
+    2 & Unpopular Youtube & 19 & 3 & 3  \\ \hline
+      & Popular Youtube   & 19 & 18 & 18  \\ \hline
       & Twitch.tv         & 148 & 150 & 150  \\ \hline
       & Soundcloud        & 148 & 148 & 148  \\ \hline
-    3 & Unpopular YouTube & 19 & 3 & 3  \\ \hline
-      & Popular YouTube   & 20 & 18 & 18 \\ \hline
+    3 & Unpopular Youtube & 19 & 3 & 3  \\ \hline
+      & Popular Youtube   & 20 & 18 & 18 \\ \hline
       & Twitch.tv         & 148 & 148 & 148  \\ \hline
@@
     Run & Source & Website & CDN & Content \\ \hline
-    1 & Unpopular YouTube & 9 & 7 & 16  \\ \hline
-      & Popular YouTube   & 10 & 9 & 9  \\ \hline
+    1 & Unpopular Youtube & 9 & 7 & 16  \\ \hline
+      & Popular Youtube   & 10 & 9 & 9  \\ \hline
       & Twitch.tv         & 12 & 13 & 13  \\ \hline
       & Soundcloud        & 11 & 17 & 17  \\ \hline
-    2 & Unpopular YouTube & 10 & 7 & 7  \\ \hline
-      & Popular YouTube   & 9 & 9 & 9  \\ \hline
+    2 & Unpopular Youtube & 10 & 7 & 7  \\ \hline
+      & Popular Youtube   & 9 & 9 & 9  \\ \hline
       & Twitch.tv         & 13 & 13 & 13  \\ \hline
       & Soundcloud        & 11 & 16 & 16  \\ \hline
-    3 & Unpopular YouTube & 10 & 7 & 7  \\ \hline
-      & Popular YouTube   & 9 & 9 & 9  \\ \hline
+    3 & Unpopular Youtube & 10 & 7 & 7  \\ \hline
+      & Popular Youtube   & 9 & 9 & 9  \\ \hline
       & Twitch.tv         & 12 & 12 & 12  \\ \hline
@@
     Run & Source & Content    \\ \hline
-    1 & Unpopular YouTube & 1525.8 \\ \hline
-      & Popular YouTube   & 9799.7 \\ \hline
+    1 & Unpopular Youtube & 1525.8 \\ \hline
+      & Popular Youtube   & 9799.7 \\ \hline
       & Twitch.tv         & 11427.8 \\ \hline
       & Soundcloud        & - \\ \hline
-    2 & Unpopular YouTube & 4331.5 \\ \hline
-      & Popular YouTube   & 9820.2 \\ \hline
+    2 & Unpopular Youtube & 4331.5 \\ \hline
+      & Popular Youtube   & 9820.2 \\ \hline
       & Twitch.tv         & 11397.1 \\ \hline
       & Soundcloud        & - \\ \hline
-    3 & Unpopular YouTube & 11274.2 \\ \hline
-      & Popular YouTube   & 9175.0 \\ \hline
+    3 & Unpopular Youtube & 11274.2 \\ \hline
+      & Popular Youtube   & 9175.0 \\ \hline
       & Twitch.tv         & 11325.4 \\ \hline
@@
 Being a significantly higher-bandwidth connection than what is available to a home user, this test over UCT's network makes the effects of caching and performance of CDNs more pronounced.
-Note the difference in throughput for the unpopular YouTube video on the first run to the second and third runs.
+Note the difference in throughput for the unpopular Youtube video on the first run to the second and third runs.
 On run 1 the video is not cached (as is evident by the higher RTT) and is delivered at a bitrate far below what the connection supports.
@@
 
-Another trend to take note of is that the throughput recorded for Twitch.tv is actually significantly higher than that of YouTube, even for very popular videos.
-This is surprising since the Twitch.tv content is not being delivered from a server residing on the African continent, while the popular YouTube content is being delivered from caches within Cape Town.
+Another trend to take note of is that the throughput recorded for Twitch.tv is actually significantly higher than that of Youtube, even for very popular videos.
+This is surprising since the Twitch.tv content is not being delivered from a server residing on the African continent, while the popular Youtube content is being delivered from caches within Cape Town.
 
 \section{Future Work}\label{sec:futurework}
-Our experiments have focussed on streaming of internet video and audio on-demand, from websites including YouTube, Twitch.tv and Soundcloud.
-In future work we would like to extend this to streaming of live video and audio content such as from YouTube Live or Twitch.tv's live streams.
-Another extension would be to consider the differences in performance of streamed video content to video adverts, which are prevalent both on YouTube and Twitch.tv.
+Our experiments have focussed on streaming of internet video and audio on-demand, from websites including Youtube, Twitch.tv and Soundcloud.
+In future work we would like to extend this to streaming of live video and audio content such as from Youtube Live or Twitch.tv's live streams.
+Another extension would be to consider the differences in performance of streamed video content to video adverts, which are prevalent both on Youtube and Twitch.tv.
 

### 2016-08-28 Writeup/paper.tex
Minor improvement to sentence
Add conclusions to abstarct

--- 2016-08-28 Writeup/paper.tex
@@
 We analyse the performance impact of these networks from the point of view both of the home user and large-scale institutions.
+We find that the majority of unpopular videos are not cached within South Africa.
+The video has to be obtained from a Google cache in Europe.
+We find that after viewing the unpopular video it is cached on both on the ISP's server and Google's South African cache.
+Subsequent views from the same ISP come from the ISP cache and views from another ISP come from Google's South African cache instead of from Europe.
+On the institutional network we find that even though, on the second execution, an unpopular YouTube video is obtained from the institution's cache, the throughput is always slower than the third execution.
 \end{abstract}
@@
 
-We tested from a number of ISPs on a home network as well as an institutional network.
+We executed our tool on various multimedia services using a number of ISPs on a home network as well as an institutional network.
 Our results gained insights on the caching behaviour of YouTube with respect to videos with very few views.

### 2016-08-28 Writeup/paper.tex
Minor tweak

@@
 Subsequent views from the same ISP come from the ISP cache and views from another ISP come from Google's South African cache instead of from Europe.
-On the institutional network we find that even though, on the second execution, an unpopular YouTube video is obtained from the institution's cache, the throughput is always slower than the third execution.
+On the institutional network we find that even though, on the second view, an unpopular YouTube video is obtained from the institution's cache, the throughput is always slower than the third view.
 \end{abstract}

### 2016-08-28 Writeup/paper.tex
Update abstact conclusions

@@
 We analyse the performance impact of these networks from the point of view both of the home user and large-scale institutions.
-We find that the majority of unpopular videos are not cached within South Africa.
-The video has to be obtained from a Google cache in Europe.
-We find that after viewing the unpopular video it is cached on both on the ISP's server and Google's South African cache.
-Subsequent views from the same ISP come from the ISP cache and views from another ISP come from Google's South African cache instead of from Europe.
-On the institutional network we find that even though, on the second view, an unpopular YouTube video is obtained from the institution's cache, the throughput is always slower than the third view.
+We find that the less popular YouTube content is not cached in South Africa, instead needing to be retrieved from Europe.
+We also find that the performance increase from local YouTube caches improves across multiple retrievals instead of just one.
 \end{abstract}
